---
title: "Age at diagnosis, updated by steven bright"
author: "Steven Bright"
date: "19/08/2022"
output: html_document
---

## Standards
All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (e.g. GLAD/EDGI/NBR) all caps
Capitalised first word
Chunk names MUST be unique

Add only one empty line between chunks
Add one extra line when starting a new section
Use hash syntax as appropriate for headings and subheadings, as per markdown syntax

Points requiring user input are enclosed thus <>

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in paths file}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovedata_scripts, "functions/add_numeric.R"))
source(file = paste0(ilovedata_scripts, "functions/remove_duplicates.R"))
source(file = paste0(ilovedata_scripts, "functions/sumscores.R"))
source(file = paste0(ilovedata_scripts, "functions/package_check.R"))
source(file = paste0(ilovedata_scripts, "functions/imp_check.R"))
source(file = paste0(ilovedata_scripts, "functions/recode_check.R"))
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "Amelia",
              "gtsummary",
              "lubridate",
              "tidyverse")

package_check(packages)
```

# Read in the data: Full Name of Questionnaire/Demographic
Change this heading to the name of your questionnaire/demographic
Load GLAD data first, then EDGI, then NBR, then RAMP

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For created variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (GLAD, EDGI, NBR, RAMP) where appropriate

## EDGI data

```{r EDGI load mhd data}
edgi_dat <- read_rds(
  file = paste0(ilovedata, "/data_raw/2022-09-16/edgi/mhd_edgi.rds")
  )
  
# Check variable names in dataframe
edgi_dat %>%
  colnames()

# Inspect dimensions of dataframe 
edgi_dat %>%
  dim()

# Report counts of duplicates in ID column
edgi_dat %>%
  select(externalDataReference) %>%
  filter(duplicated(.)) %>%
  count(., externalDataReference)

# Report number of IDs to be dropped
edgi_excluded <- edgi_dat %>%
  select(externalDataReference) %>%
  filter(duplicated(.)) %>%
  count(., externalDataReference) %>%
  select("EDGI Dropped IDs" = "n") %>%
  colSums() + 1

edgi_excluded
```

```{r EDGI load dem data}
edgi_dem_dat <- read_rds(
  file = paste0(ilovedata, "/data_raw/2022-09-16/edgi/dem_edgi.rds")
)

# Check variable names in dataframe
edgi_dem_dat %>% 
  colnames()

# Inspect dimensions of dataframe 
edgi_dem_dat %>% 
  dim()

# Report counts of duplicates in ID column
edgi_dem_dat %>% 
  select(externalDataReference) %>%
  filter(duplicated(.)) %>%
  count(., externalDataReference)

# Report number of IDs to be dropped
edgi_dem_excluded <- edgi_dem_dat %>%
  select(externalDataReference) %>%
  filter(duplicated(.)) %>%
  count(., externalDataReference) %>%
  select("EDGI Dropped IDs" = "n") %>%
  colSums() + 1

edgi_dem_excluded
```

Select/rename relevant columns and de-duplicate/NA-remove ID column
NB: If this is data from the COPING survey, add "_cop" to the end of each variable name, including startDate/endDate
```{r EDGI select}
edgi_dat_id <- edgi_dat %>% #new dataset with ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "EDGI",
             .after = "externalDataReference") %>% # Create new sample column
  dplyr::rename(
    "ID" = "externalDataReference"
  ) %>% 
  select(
    ID,
    sample,
    startDate,
    endDate,
    mhd.anorexia_nervosa.2,
    mhd.atypical_anorexia_nervosa.2,
    mhd.bulimia_nervosa.2,
    mhd.atypical_bulimia_nervosa.2,
    mhd.bingeeating_disorder.2,
    mhd.atypical_bingeeating_disorder.2,
    mhd.purging_disorder.2,
    mhd.nighteating_syndrome.1,
    mhd.pica.2,
    mhd.avoidantrestrictive_food_intake_disorder.2,
    mhd.rumination_eating_disorder.1,
    mhd.other_eating_disorder.2,
    mhd.other_specified_feeding_or_eating_disorder.1
  )

# Inspect colnames
edgi_dat_id %>%
  colnames()

# Inspect dimensions of new data set
edgi_dat_id %>%
  dim()
```

```{r EDGI dem select}
edgi_dem_dat_id <- edgi_dem_dat %>% #new dataset with ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "EDGI",
             .after = "externalDataReference") %>% # Create new sample column
  dplyr::rename(
    "ID" = "externalDataReference"
  ) %>% 
  select(
    ID, # Dropping sample, startDate and endDate before full_join with edgi mhd data
    dem.day,
    dem.month,
    dem.year
  )

# Inspect colnames
edgi_dem_dat_id %>%
  colnames()

# Inspect dimensions of new data set
edgi_dem_dat_id %>%
  dim()
```

```{r Join EDGI mhd and dem data}
edgi_dat_id <- edgi_dat_id %>% 
  full_join(edgi_dem_dat_id,
            by = "ID")

#Check data
edgi_dat_id %>% 
  head()

edgi_dat_id %>% 
  dim()
```

Check missingness by missmap
```{r EDGI missmap}
edgi_dat_id %>% 
  missmap()
```

# Cleaning and creating dob variable

Some of the responses in the age at diagnosis variables are the year at which 
the participant was diagnosed instead of their age. Therefore, we need to 
calculate the participants date of birth to work out their age at diagnosis.

I've taken and adapted some code from Abi and Jess' age cleaning script to do this.

```{r Check distribution of dem.day month and year variables}
dob_vars <- edgi_dat_id %>% 
  select(contains("dem.")) %>% 
  colnames()

dob_vars %>% 
  map(
    function(
      variable_name){
    group_by_at(
      edgi_dat_id, variable_name) %>% 
      summarise(Count = n()) %>% 
      as_tibble()
  }
  )
```

```{r set minimum and maximum values for dem.day month and year}
# Day
day.min.scale = 1
day.max.scale = 31

# Month
month.min.scale = 1
month.max.scale = 12

# Year
year.min.scale = 1899
year.max.scale = 2022 # note max age set later in age_upper_limit
```

```{r Add years to birthyear}
#add values to birth year
edgi_dat_id <- edgi_dat_id %>%
  mutate(dem.year = 
           dem.year + 1919)

# check EDGI
edgi_dat_id %>%
  group_by(dem.year) %>% 
  count()
```

```{r Clean dem.day}
edgi_dat_id <- edgi_dat_id %>% 
  mutate(dem.day =
           case_when(dem.day < day.min.scale | dem.day > day.max.scale ~ -666, # implausible value
                     TRUE ~ dem.day)
         ) # leave as is


# Check for implausible values
edgi_dat_day_imp_n <- edgi_dat_id %>% 
  filter(dem.day == -666) %>% 
  nrow()

# Check
edgi_dat_day_imp_n

# If statement
if (edgi_dat_day_imp_n == 0) {
  print(paste0("The number of implausible values in the GLAD day of birth variable is ", edgi_dat_day_imp_n, ". This is fine."))
} else {
  print(paste0("The number of implausible values in the GLAD day of birth variable is ", edgi_dat_day_imp_n, ". Please investigate."))
}

# Check cleaned variable
edgi_dat_id %>% 
  group_by(dem.day) %>% 
  count(dem.day) # The outlier is 59 (1 observation)
```

```{r GLAD & EDGI Clean dem.month}
edgi_dat_id <- edgi_dat_id %>% 
  mutate(dem.month =
           case_when(dem.month < month.min.scale | dem.month > month.max.scale ~ -666, # implausible value
                     TRUE ~ dem.month)
         ) # leave as is

# Check for implausible values
edgi_dat_month_imp_n <- edgi_dat_id %>% 
  filter(dem.month == -666) %>% 
  nrow()

# Check
edgi_dat_month_imp_n

# If statement
if (edgi_dat_month_imp_n == 0) {
  print(paste0("The number of implausible values in the GLAD month of birth variable is ", edgi_dat_month_imp_n, ". This is fine."))
} else {
  print(paste0("The number of implausible values in the GLAD month of birth variable is ", edgi_dat_month_imp_n, ". Please investigate."))
}

# Check clean variable
edgi_dat_id %>% 
  group_by(dem.month) %>% 
  count()
```

```{r Clean dem.year}
edgi_dat_id <- edgi_dat_id %>% 
  mutate(dem.year =
           case_when(dem.year < year.min.scale | dem.year > year.max.scale ~ -666, # implausible value
                     dem.year == 2020 ~ -666,
                     TRUE ~ dem.year)
         )

# Check for implausible values
edgi_year_imp_n <- edgi_dat_id %>% 
  filter(dem.year == -666) %>% 
  nrow()

# Check
edgi_year_imp_n

# If statement
if (edgi_year_imp_n == 0) {
  print(paste0("The number of implausible values in the GLAD year of birth variable is ", edgi_year_imp_n, ". This is fine."))
} else {
  print(paste0("The number of implausible values in the GLAD year of birth variable is ", edgi_year_imp_n, ". Please investigate."))
}

# Check
edgi_dat_id %>% 
  group_by(dem.year) %>% 
  count() # implausible years are 2020 and 2034 (latter was changed to -666)
```

```{r Change all -666 to NA }
edgi_dat_id <- edgi_dat_id %>%
  mutate_if(is.numeric, ~na_if(., -666)) # Implausible value

#Check result
edgi_dat_id %>% 
  filter(if_all(c(dem.day, dem.month, dem.year),
                ~ .x == -666))
```

```{r Make birth date}
edgi_dat_id <- edgi_dat_id %>%
  mutate(dem.dob = make_date(dem.year, dem.month, dem.day))

# check
edgi_dat_id %>% 
  select(dem.day,
         dem.month,
         dem.year,
         dem.dob) %>% 
  head()
```

```{r Put EDGI age at diagnosis variables into a vector}
edgi_age_at_diagnosis_vars <- edgi_dat_id %>% 
  select(contains("mhd.")) %>% 
  colnames()

#Check names
edgi_age_at_diagnosis_vars
```

```{r See distribution of all age at diagnosis variables across EDGI}
edgi_age_at_diagnosis_vars %>% 
  map(function(variable_name){
    group_by_at(edgi_dat_id, variable_name) %>% 
      summarise(Count = n()) %>% 
      as_tibble()
  })
```

One pt who answered "2018" to mhd.anorexia_nervosa.2 and mhd.bulimia_nervosa.2 
was born in 1994, so they get 24 at age of diagnosis.

One pt who answered 2013 to mhd.bingeeating_disorder.2 was born in 1985,
so they get 28 for age at diagnosis.

Note: the mhd variables only have the year of diagnosis. Therefore, unable 
to ascertain whether the pt's birthday in that year would have passed or not.

```{r Check erroneous year values against dob}
edgi_dat_id %>% 
  filter(mhd.anorexia_nervosa.2 == 2018 &
           mhd.bulimia_nervosa.2 == 2018) %>% 
  select(dem.dob)

edgi_dat_id %>% 
  filter(mhd.bingeeating_disorder.2 == 2013) %>% 
  select(dem.dob)
```

```{r Change year answers in age at diagnosis to age}
#Anorexia nervosa
edgi_dat_id <- edgi_dat_id %>% 
  mutate(mhd.anorexia_nervosa.2 = 
           case_when(
             mhd.anorexia_nervosa.2 == 2018 ~ 24,
             mhd.anorexia_nervosa.2 != 2018 ~ mhd.anorexia_nervosa.2
           ))

#Bulimia nervosa
edgi_dat_id <- edgi_dat_id %>% 
  mutate(mhd.bulimia_nervosa.2 = 
           case_when(
             mhd.bulimia_nervosa.2 == 2018 ~ 24,
             TRUE ~ mhd.bulimia_nervosa.2
           )
         )

#Binge eating
edgi_dat_id <- edgi_dat_id %>% 
  mutate(mhd.bingeeating_disorder.2 = 
           case_when(
             mhd.bingeeating_disorder.2 == 2013 ~ 28,
             TRUE ~ mhd.bingeeating_disorder.2
           )
         )

#Check data
edgi_age_at_diagnosis_vars %>% 
  map(function(variable_name){
    group_by_at(edgi_dat_id, variable_name) %>% 
      summarise(Count = n()) %>% 
      as_tibble()
  }
  )
```

# Cleaning age at diagnosis variables

```{r Add exclude cols for the age at diagnosis cleaning}
edgi_dat_id_cols <- edgi_dat_id %>% 
  colnames()

edgi_exclude_cols <- edgi_dat_id %>% 
  select(!contains("mhd.")) %>% 
  colnames()

#Check vars
edgi_dat_id_cols
edgi_exclude_cols
```

Age at diagnosis outliers: 
- Lower: Should there be a lower limit for being diagnosed with an ED?
- Upper: The oldest person in the world is 117 years.

```{r GLAD & EDGI current age define limits}
age_lower_limit = 1 #Put as 1 for now
age_upper_limit = 100 #Put as 100 for now
```

```{r GLAD & EDGI age outlier count}
edgi_dat_id %>% 
  map2(edgi_dat_id_cols,
          function(column, column_name){
            if(column_name %in% edgi_exclude_cols){
              print(NA_real_)
            } else {
              length(which(column > age_upper_limit |
                       column < age_lower_limit &
                         column != -77))
            }
          })
```

```{r Recode age outliers to -666}
#If the pt's age value is greater than the upper limit or less than the lower limit, they get -666
edgi_dat_id <- edgi_dat_id %>% 
  map2_df(edgi_dat_id_cols,
          function(column, column_name){
            if(column_name %in% edgi_exclude_cols){
              column
            } else{
                case_when(
                  column == -77 ~ -777,
                  column > age_upper_limit |
                    column < age_lower_limit ~ -666,
                  TRUE ~ column
                )
            }
          })

#Check results
edgi_age_at_diagnosis_vars %>% 
  map(function(variable_name){
    group_by_at(edgi_dat_id, variable_name) %>% 
      summarise(Count = n()) %>% 
      as_tibble()
  })
```

```{r Round age at diagnosis values to whole numbers}
#Note: Rounding should change ages such as 18.41 to 18
edgi_dat_id <- edgi_dat_id %>% 
  map2_df(edgi_dat_id_cols,
       function(column, column_name){
         if(column_name %in% edgi_exclude_cols){
           column
         } else {
           column <- round(column)
         }
       }
       )

#Re-inspect distribution of age at diagnoses variables
edgi_age_at_diagnosis_vars %>% 
  map(function(variable_name){
    group_by_at(edgi_dat_id, variable_name) %>% 
      summarise(Count = n()) %>% 
      as_tibble()
  }
  )
```

```{r Change all -666 to NA }
edgi_dat_id <- edgi_dat_id %>%
  mutate_if(
    is.numeric, 
    ~na_if(., -666)
    ) # Implausible value

#Check result
edgi_dat_id %>% 
  filter(
    if_all(
      c(dem.day, dem.month, dem.year), 
      ~ .x == -666)
    )
```

# Combining Data

Bind rows of GLAD, EDGI, NBR and RAMP data
Read in data, bind datasets, then clean all together
```{r Merge data sets}
dat <- edgi_dat_id

#dat <- glad_dat_id %>%
#  bind_rows(edgi_dat_id, nbr_dat_id, ramp_dat_id)

# Check dat using glimpse before continuing
#dat %>% glimpse()
```

Extract and save labels
```{r Extract save labels}
# Save variable labels
question_labels <- sjlabelled::get_label(dat)

# Save value labels
answer_labels <- sjlabelled::get_labels(dat, values = "as.name")

# Change -77 to -777 in value labels names
chng <- rapply(sapply(answer_labels, names),
               function(x) ifelse(x==-77, -777, x),
               how = "replace")

# Add multiple lines here as necessary to change other nonanswer values in labels
# chng <- rapply(chng,
#                function(x) ifelse(x==-88, -888, x),
#                how = "replace")

# Substitute new value labels into answer_labels
for (i in 1:length(chng)){
  if(!is.null(answer_labels[[i]])){
  names(answer_labels[[i]]) <- chng[[i]]
  }
}
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(where(is.numeric),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)
                )
         )

# Re-add labels after mutate
dat <- sjlabelled::set_label(dat, question_labels)
dat <- sjlabelled::set_labels(dat, labels = answer_labels)
```

Create list of all labels and attributes
This chunk supersedes all categorical/numeric cleaning
It gives you an output of c(the question label, all value-label pairs)
for each variable
Check for errors in the output of this chunk, including:
- Label spelling errors (for questions and answers)
- Incorrect values
- Mismatches between labels and values
- Scale errors
- Variable naming issues from the data extraction
- Any other issues you can see
All issues/changes need to be logged as a to-do on Teams with yourself and Saakshi/Mika tagged
At this point, you also need to pick out any continuous, date or text variables 
to be cleaned in the later chunks
```{r List labels attrs}
label_list <- sapply(dat, function(x) c(attr(x, "label"), attr(x, "labels")))
label_list
```

# Save cleaned data

Combined object for excluded participants
```{r GLAD EDGI NBR save excluded participants}
#glad_edgi_nbr_excluded <- as.data.frame(cbind(glad_excluded, edgi_excluded, nbr_excluded))
#glad_edgi_nbr_excluded
```

```{r Created vector of desired variable names}
desired_variables <- dat %>% 
  select(ID,
         sample,
         startDate,
         endDate,
         contains("mhd.")) %>% 
  colnames()

#Check vars
desired_variables
```

# EDGI
```{r Write cleaned EDGI variables to a .rds file}
dat %>% 
  select(all_of(desired_variables)) %>% 
  saveRDS(
    file = paste0(ilovedata,"/EDGI_protocol/data/demographics/age_at_diagnosis_edgi_clean.rds")
    )
```
