---
title: "Age ( EDGI sign-ups)"
author: "Abigail ter Kuile & Jessica Mundy"
date: "28/06/2021"
output: html_document
---

# Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

## Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in paths file}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovedata_scripts, "functions/add_numeric.R"))
source(file = paste0(ilovedata_scripts, "functions/remove_duplicates.R"))
source(file = paste0(ilovedata_scripts, "functions/sumscores.R"))
source(file = paste0(ilovedata_scripts, "functions/package_check.R"))
source(file = paste0(ilovedata_scripts, "functions/imp_check.R"))
source(file = paste0(ilovedata_scripts, "functions/recode_check.R"))
```

Note: always load tidyverse last
```{r Install load dependencies}
packages = c(
  "summarytools",
  "sjlabelled",
  "data.table",
  "Amelia",
  "lubridate",
  "gtsummary",
  "tidyverse"
  )
package_check(packages)
```

## Retrieve the recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date = Sys.Date()
date
```

# Read in the data: Demographic
## EDGI data
Please do not change the name of the object so it remains universal
```{r EDGI read in data}
edgi_dat <- read_rds(
  file = paste0(ilovedata, "/data_raw/2022-09-16/edgi/dem_edgi.rds")
  )
  
# Check variable names in dataframe
edgi_dat %>%
  colnames()

# Inspect dimensions of dataframe 
edgi_dat %>%
  dim()
```

Select & rename relevant columns (will be a function at some point)
```{r EDGI select & rename relevant columns}

edgi_dat_id <- edgi_dat %>% # New dataset with ID
  drop_na(externalDataReference) %>% # # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "EDGI",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference,# ID
         sample,
         startDate,
         endDate,
         dem.how_old_are_you_now.txt, # age at sign-up (self-reported)
         dem.day, # day of birth
         dem.month, # month of birth
         dem.year # year of birth
         ) %>% 
   
  rename_with( ~ paste(.x, "unc", sep = "_"), starts_with("dem"))
  
# Inspect colnames
edgi_dat_id %>%
  colnames()
```

Look at number of people excluded
```{r EDGI number excluded}
# Inspect dimensions of new data set
edgi_dat_id %>%
  dim()

# Inspect number of rows dropped
edgi_excluded <- dim(edgi_dat_id)[1]-dim(edgi_dat)[1]
edgi_excluded

```

Check missingness by missmap
```{r EDGI inspect missingness}
 edgi_miss_map <- edgi_dat_id %>% 
   missmap()
edgi_miss_map
```

Rename data
```{r rename data}
dat <- edgi_dat_id 
```

# Clean EGDI age variables

### EDGI Inspect age variable
```{r EDGI check values}
dat %>%
  freq(dem.how_old_are_you_now.txt_unc)
```

### Convert negative values of age to positive values and convert to numeric (this helps bind all datatsets at the end)
```{r  EDGI dem.how_old_are_you_now.txt_unc conversion to positive value}
dat <- dat %>%
  mutate(
    dem.how_old_are_you_now.txt_unc =
      abs(
        as.numeric(
        dem.how_old_are_you_now.txt_unc)
      )
  )
#Check
dat %>%
  
  freq(dem.how_old_are_you_now.txt_unc)
```
Age outliers: 
- Lower: The data set should not have individuals younger than 16 (requirement of GLAD)
- Upper: The oldest person in the world is 117 years.

###  EDGI Set age limits
```{r  EDGI current age define limits}
age_lower_limit = 16
age_upper_limit = 117
```

###  EDGI Check for number of outliers in age variable
```{r  EDGI age outlier count}
dat %>%
  filter(
    dem.how_old_are_you_now.txt_unc > age_upper_limit | # older than the age limit
      dem.how_old_are_you_now.txt_unc < age_lower_limit # younger than the age limit
    ) %>%
  nrow()
```

###  EDGI Recode age outliers to -666
```{r  EDGI age Recode outliers to -666}
dat <- dat %>%
  mutate(dem.how_old_are_you_now.txt =
      case_when(
        dem.how_old_are_you_now.txt_unc == -777 ~ -777,
        dem.how_old_are_you_now.txt_unc == -999 ~ -999,
        dem.how_old_are_you_now.txt_unc == -888 ~ -888,
        (dem.how_old_are_you_now.txt_unc > age_upper_limit |
          dem.how_old_are_you_now.txt_unc < age_lower_limit ) ~ -666,
        TRUE ~ dem.how_old_are_you_now.txt_unc
      )
  )

```

###  EDGI Inspect clean age variable
```{r  EDGI age after recoding to -666}
dat %>%
  freq(dem.how_old_are_you_now.txt)
```

##  EDGI age at sign up (based on DOB)

###  EDGI Inspect variables
```{r  EDGI Inspect variables}
dat %>% 
  freq(dem.day_unc)

dat %>% 
  freq(dem.month_unc)

dat %>% 
  freq(dem.year_unc)
```
###Convert day, month, year to numeric and negative values to positive values (this helps bind datatsets)
Day conversion numeric and positive values
```{r  EDGI dem.day.unc conversion to positive values and numeric}
dat <- dat %>%
  mutate(
    dem.day_unc =
      abs(
        as.numeric(
        dem.day_unc)
      )
  )
#Check
dat %>%
  freq(dem.day_unc)
```

Month conversion numeric and positive values
```{r  EDGI dem.month_unc conversion to positive values and numeric}
dat <- dat %>%
  mutate(
    dem.month_unc =
      abs(
        as.numeric(
        dem.month_unc)
      )
  )
#Check
dat %>%
  freq(dem.month_unc)
```

Year conversion numeric and positive values
```{r  EDGI dem.year_unc conversion to positive values and numeric}
dat <- dat %>%
  mutate(
    dem.year_unc =
      abs(
        as.numeric(
        dem.year_unc)
      )
  )
#Check
dat %>%
  freq(dem.year_unc) 
```

###  EDGI Add values to birthyear 

Note: GLAD and EDGI dem.year is coded differently. 1 = 1900 in GLAD, and 1 = 1920 in EDGI. Check frequencies separately and compare once converted in next chunk 
```{r year GLAD EDGI check frequencies separatly}
dat %>%
  group_by(sample) %>%
  freq(dem.year_unc)
```

###  EDGI Add values to birthyear 
GLAD: values are given as e.g. 1-119 which needs to be converted to 1901-2019 (add 1899 years)
EDGI: values are given as 1-101 which needs to be converted to 1920-2020 (add 1919 years)
```{r  EDGI Add years to birthyear}
#add values to birth year
dat <- dat %>%
  mutate(dem.year_unc = if_else(sample == "GLAD",
                                dem.year_unc + 1899,
                                dem.year_unc + 1919)) ##if GLAD add 1899, if EDGI add 1919

# check GLAD
dat %>%
  filter(sample == "GLAD") %>%
  freq(dem.year_unc)
# check EDGI
dat %>%
  filter(sample == "EDGI") %>%
  freq(dem.year_unc)
  
```
###  EDGI set minimum and maximum values
```{r  EDGI set minimum and maximum values}
# Day
day.min.scale = 1
day.max.scale = 31

# Month
month.min.scale = 1
month.max.scale = 12

# Year
year.min.scale = 1899
year.max.scale = 2021 # note max age set later in age_upper_limit
```

###  EDGI Clean dem.day
```{r  EDGI Clean dem.day}
dat <- dat %>% 
  mutate(dem.day_unc_clean =
           case_when(dem.day_unc < day.min.scale | dem.day_unc > day.max.scale ~ -666, # implausible value
                     TRUE ~ dem.day_unc)
         ) # leave as is


# Check for implausible values
dat_day_imp_n <- dat %>% 
  filter(dem.day_unc_clean == -666) %>% 
  nrow()

# Check
dat_day_imp_n

# If statement
if (dat_day_imp_n == 0) {
  print(paste0("The number of implausible values in the GLAD day of birth variable is ", dat_day_imp_n, ". This is fine."))
  setnames(dat,
         old = "dem.day_unc_clean",
         new = "dem.day")
} else {
  print(paste0("The number of implausible values in the GLAD day of birth variable is ", dat_day_imp_n, ". Please investigate."))
  setnames(dat,
         old = "dem.day_unc_clean",
         new = "dem.day")
}

# Check
colnames(dat)

# Check cleaned variable
dat %>% 
  freq(dem.day) 
```
There is one implausible value (59) in the EDGI dem data set which has been recoded to -666

###  EDGI Clean dem.month
```{r  EDGI Clean dem.month}
dat <- dat %>% 
  mutate(dem.month_unc_clean =
           case_when(dem.month_unc < month.min.scale | dem.month_unc > month.max.scale ~ -666, # implausible value
                     TRUE ~ dem.month_unc)
         ) # leave as is

# Check for implausible values
dat_month_imp_n <- dat %>% 
  filter(dem.month_unc_clean == -666) %>% 
  nrow()

# Check
dat_month_imp_n

# If statement
if (dat_month_imp_n == 0) {
  print(paste0("The number of implausible values in the GLAD month of birth variable is ", dat_month_imp_n, ". This is fine."))
  setnames(dat,
         old = "dem.month_unc_clean",
         new = "dem.month")
} else {
  print(paste0("The number of implausible values in the GLAD month of birth variable is ", dat_month_imp_n, ". Please investigate."))
  setnames(dat,
         old = "dem.month_unc_clean",
         new = "dem.month")
}

# Check
colnames(dat)

# Check clean variable
dat %>% 
  freq(dem.month)
```
The month variable should now be clean.

###  EDGI Clean dem.year
```{r  EDGI dem Clean dem.year}
dat <- dat %>% 
  mutate(dem.year_unc_clean =
           case_when(dem.year_unc < year.min.scale | dem.year_unc > year.max.scale ~ -666,  # implausible value
                     TRUE ~ dem.year_unc)
         )

# Check for implausible values
glad_edgi_year_imp_n <- dat %>% 
  filter(dem.year_unc_clean == -666) %>% 
  nrow()

# Check
glad_edgi_year_imp_n

# If statement
if (glad_edgi_year_imp_n == 0) {
  print(paste0("The number of implausible values in the GLAD year of birth variable is ", glad_edgi_year_imp_n, ". This is fine."))
  setnames(dat,
         old = "dem.year_unc_clean",
         new = "dem.year")
} else {
  print(paste0("The number of implausible values in the GLAD year of birth variable is ", glad_edgi_year_imp_n, ". Please investigate."))
  setnames(dat,
         old = "dem.year_unc_clean",
         new = "dem.year")
}

# Check
dat %>% 
  freq(dem.year)


```
There is one implausible value (year 2034) in the EDGI dem year data set which has been recoded to -666

dat = clean data set, all implausible values are set to -666
However, we need to drop these values to NA in order to calculate DOB (needed for the next steps)

#  EDGI Create a new data set where implausible values are dropped to NA

##  EDGI Drop all -666 to NA
```{r  EDGI Drop all -666 to NA }
dat_no_imps <- dat %>%
  mutate_if(is.numeric, ~na_if(., -666)) # Implausible value
```

##  EDGI Drop all variables with "_unc" on the end
```{r  EDGI Drop all variables with "_unc" on the end}
dat_clean <- dat_no_imps %>% 
  select(!contains("_unc")) # selects ID, sample and drops all uncleaned variables

# Check (there should be no variables with "_unc" in the name now)
colnames(dat_clean)
```

###  EDGI Create age variable
Use lubridate for this:
```{r  EDGI make birth date}
dat_clean <- dat_clean %>%
  mutate(dem.dob = make_date(dem.year, dem.month, dem.day))

# check
dat_clean %>% 
  select(dem.day,
         dem.month,
         dem.year,
         dem.dob) %>% 
  head()
```

###  EDGI calculate age from birth date and startdate
note: using startdate instead of enddate and this increases N (only slightly in GLAD and EDGI, but in NBR it increases by ~2k). It also matched self-report age at sign up more closely (increases the match between self-report age and dob age slightly)
This will be their age at the time they did the questionnaire
```{r  EDGI calculate age from birth date and startdate}
dat_clean$dem.dob_age <- interval(
    start = dat_clean$dem.dob,
    end = dat_clean$startDate) %/% # use modulo to round down by %/%
        duration(num = 1, units = "years")


# check GLAD 
dat_clean %>%
  filter(sample == "GLAD") %>% 
  select(dem.dob,
         dem.dob_age,
         dem.how_old_are_you_now.txt) %>% 
  head()

# check EDGI 
dat_clean %>%
  filter(sample == "EDGI") %>% 
  select(dem.dob,
         dem.dob_age,
         dem.how_old_are_you_now.txt) %>% 
  head()
  
```
#Inspect difference self-report age and DOB age
```{r difference self-report age and DOB age}
# check GLAD 
dat_clean %>%
  filter(
    dem.dob_age != dem.how_old_are_you_now.txt, sample == "GLAD") %>% 
  select(dem.dob,
         dem.dob_age,
         dem.how_old_are_you_now.txt,
         dem.year) 

# check EDGI
dat_clean %>%
  filter(
    dem.dob_age != dem.how_old_are_you_now.txt, sample == "EDGI") %>% 
  select(dem.dob,
         dem.dob_age,
         dem.how_old_are_you_now.txt,
         dem.year) 
```
+++ATK: do we want to do something about those who's dob ages don't match their self-report ages?

###  EDGI Convert dem.dob_age to numeric and negative values to positive values (this helps bind all datatsets at the end)
```{r  EDGI dem.dob_age conversion to positive values and numeric}
dat_clean <- dat_clean %>%
  mutate(
    dem.dob_age =
      abs(
        as.numeric(
        dem.dob_age)
      )
  )
#Check
dat_clean %>%
  freq(dem.dob_age)
```

###  EDGI Check for number of outliers in DOB age at sign up variable using age limits
Same age limit as used in earlier chunk for self-reported age:
age_lower_limit = 16
age_upper_limit = 117
```{r  EDGI DOB age at sign up outlier count}
dat_clean %>%
  filter(
    dem.dob_age > age_upper_limit | # older than the age limit
      dem.dob_age < age_lower_limit # younger than the age limit
    ) %>%
  nrow()
```

###  EDGI Recode DOB age at sign up at sign up outliers to -666
```{r  EDGI DOB age at sign up Recode outliers to -666}
dat_clean <- dat_clean %>%
  mutate(dem.dob_age =
      case_when(
        dem.dob_age == -777 ~ -777,
        dem.dob_age == -999 ~ -999,
        dem.dob_age == -888 ~ -888,
        (dem.dob_age > age_upper_limit |
          dem.dob_age < age_lower_limit ) ~ -666,
        TRUE ~ dem.dob_age
      )
  )

```

###  EDGI Inspect clean DOB age at sign up at sign up variable
```{r  EDGI DOB age at sign up after recoding to -666}
dat_clean %>%
  freq(dem.dob_age)
```
# Deal with missing age data and ages that do not match up
```{r Get frequencies of whether the two age variables match}
dat_clean <- dat_clean %>% 
  mutate(dem.age_match =
           case_when(!is.na(dem.how_old_are_you_now.txt) 
                     & dem.how_old_are_you_now.txt != -666 
                     & dem.how_old_are_you_now.txt == dem.dob_age 
                     & !is.na(dem.dob_age) 
                     & dem.dob_age != -666 ~ "Present ages match",
                     
                     !is.na(dem.how_old_are_you_now.txt) 
                     & dem.how_old_are_you_now.txt != -666 
                     & dem.how_old_are_you_now.txt != dem.dob_age 
                     & !is.na(dem.dob_age)
                     & dem.dob_age != -666 ~ "Present ages do not match",
                     
                     !is.na(dem.how_old_are_you_now.txt)
                     & dem.how_old_are_you_now.txt != -666
                     & (is.na(dem.dob_age) | dem.dob_age == -666) ~ "Missing DOB-derived age",
                     
                     (is.na(dem.how_old_are_you_now.txt) 
                     | dem.how_old_are_you_now.txt == -666)
                     & !is.na(dem.dob_age) & dem.dob_age != -666 ~ "Missing self-reported age",
                     
                     (is.na(dem.how_old_are_you_now.txt) 
                     | dem.how_old_are_you_now.txt == -666) 
                     & (is.na(dem.dob_age) | dem.dob_age == -666) ~ "Both ages missing")
         )

# check
dat_clean %>% 
  freq(dem.age_match)
```
```{r Look at data for participants who having missing age}
dat_clean %>% 
  filter(dem.age_match == "Missing DOB-derived age" 
         | dem.age_match == "Missing self-reported age") %>% 
  select(dem.how_old_are_you_now.txt,
         dem.dob_age)
```
They all look like reasonable ages.

Now need to create a variable which provides the more realistic age for participants if their self-reported age and DOB-derived age don't match up.
```{r Create variable for "likely" age}
dat_clean <- dat_clean %>% 
  mutate(dem.age_likely = 
           case_when(dem.age_match == "Present ages match" ~ dem.how_old_are_you_now.txt,
                     
                     dem.age_match == "Both ages missing" ~ NA_real_,
                     
                     dem.age_match == "Missing DOB-derived age" ~ dem.how_old_are_you_now.txt,
                     
                     dem.age_match == "Missing self-reported age" ~ dem.dob_age,
                     
                     dem.age_match == "Present ages do not match" 
                     & dem.how_old_are_you_now.txt < dem.dob_age ~ dem.how_old_are_you_now.txt, # choose lower of the two ages
                     
                     dem.age_match == "Present ages do not match"
                     & dem.how_old_are_you_now.txt > dem.dob_age ~ dem.dob_age) # choose lower of the two ages
         )

# check
dat_clean %>% 
  freq(dem.age_likely)
```



#Categorise age into groups (GLAD, EDGI and NBR) 
In RAMP, age is indicated categorically: 16-18, 19-25, 26-35, 36-45, 46-55, 56-65, 66-70, 71-75, 76-80, 81-85, 86-90, 91-100, 100+
Age categories in GLAD, EDGI and NBR have been created to reflect this. 
Age at sign-up calculated from DOB has been used for consistency as NBR does have self-reported age at sign up. 

##  EDGI categorise age groups
```{r  EDGI Create age groups per 10 years categories and add numeric}
dat_clean <- dat_clean %>%
  mutate(
    dem.age_category_numeric =
      case_when(
          dem.age_likely >= 16 & dem.age_likely <= 18 ~ "1",
          dem.age_likely >= 19 & dem.age_likely <= 25 ~ "2",
          dem.age_likely >= 26 & dem.age_likely <= 35 ~ "3",
          dem.age_likely >= 36 & dem.age_likely <= 45 ~ "4",
          dem.age_likely >= 46 & dem.age_likely <= 55 ~ "5",
          dem.age_likely >= 56 & dem.age_likely <= 65 ~ "6",
          dem.age_likely >= 66 & dem.age_likely <= 70 ~ "7",
          dem.age_likely >= 71 & dem.age_likely <= 75 ~ "8",
          dem.age_likely >= 76 & dem.age_likely <= 80 ~ "9",
          dem.age_likely >= 81 & dem.age_likely <= 85 ~ "10",
          dem.age_likely >= 86 & dem.age_likely <= 90 ~ "11",
          dem.age_likely >= 91 & dem.age_likely <= 100 ~ "12",
          dem.age_likely >= 101 & dem.age_likely <= 120 ~ "13" # oldest person in the world is 117 years
                )
    )
```

 EDGI convert to numeric and positive values for binding datasets
```{r  EDGI Conversion dem.age_category_numeric to numeric and positive value for binding}
dat_clean <- dat_clean %>%
  mutate(
    dem.age_category_numeric =
      abs(
        as.numeric(
          dem.age_category_numeric)
      )
  )
#Check
dat_clean %>%
  freq(dem.age_category_numeric)
```

 EDGI create categorical age groups and recode as factors from dem.age_category_numeric
```{r  EDGI categorical recode factors}

dat_clean <- dat_clean %>%
    mutate(
      dem.age_category =
        recode_factor(
          dem.age_category_numeric, 
          "1" = "16-18",
          "2" = "19-25",
          "3" = "26-35",
          "4" = "36-45",
          "5" = "46-55",
          "6" = "56-65",
          "7" = "66-70",
          "8" = "71-75",
          "9" = "76-80",
          "10" = "81-85",
          "11" = "86-90",
          "12" = "91-100",
          "13" = "+100"
        )
    )
dat_clean %>%
  freq(dem.age_category)

```

# Save cleaned data

Check colnames before exporting final dataset
```{r check colnames}
dat_clean %>% 
  colnames()
```

Save variables for exporting in clean dataset - note: DOB variables have been excluded as they contain identifiable information
```{r Save COPING variables for export}
export_variables <- dat_clean %>% 
  select(ID,
         startDate,
         endDate,
         sample,
         dem.how_old_are_you_now.txt,
         dem.dob_age,
         dem.age_match,
         dem.age_likely,
         dem.age_category,
         dem.age_category_numeric) %>%
  colnames()
```

Combined object for excluded participants
```{r GLAD EDGI save excluded participants}

edgi_excluded
```

# EDGI
```{r Write cleaned EDGI variables to a .rds file}
dat_clean %>% 
  filter(sample == "EDGI") %>%  # select only EDGI participants
  select(all_of(export_variables)) %>%
  saveRDS(
    file = paste0(ilovedata, "/EDGI_protocol/data/demographics/age_edgi_clean.rds")
    )
```

## SAVED FOR INTERNAL USE ONLY (contains dob)
# EDGI
```{r INTERNAL ONLY Write cleaned EDGI variables to a .rds file}
dat_clean %>% 
  filter(sample == "EDGI") %>%  # select only EDGI participants
  saveRDS(
    file = paste0(ilovedata, "/EDGI_protocol/data/demographics/age_edgi_clean_INTERNAL_ONLY.rds")
    )
```



