---
title: "Employment_SB"
author: "Shannon Bristow"
date: '2022-09-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "Employment"
author: "Alish Palmos"
date: "24/08/2021"
output: html_document
---

All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (e.g. GLAD/EDGI/NBR) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = "scripts/functions/add_numeric.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/imp_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovedata channel on teams}
source(file = "../credentials/paths.R")
```

# Read in the data: Employment         
Change this heading to the name of your questionnaire/demographic
Load GLAD data first, then EDGI, then NBR, then RAMP

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (GLAD, EDGI, NBR, RAMP)


# Read in data

## GLAD data
```{r GLAD load data}
glad_dat <- read_rds(
  file = paste0(ilovedata, "/data_raw//2022-09-16/glad/dem_glad.rds")
  )
  
# Check variable names in dataframe
glad_dat %>%
  colnames()
# Inspect dimensions of dataframe 
glad_dat %>%
  dim()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
```{r GLAD Specify columns to be excluded from add_numeric function}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate"
  )
```

Select & rename relevant columns
```{r GLAD Select & rename relevant columns}
glad_dat_id <- glad_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference,
           .keep_all = TRUE) %>% 
  add_column(sample = "GLAD",
             .after = "externalDataReference") %>% #create new column with sample
  select(
         ID = externalDataReference, # ID
         startDate,
         endDate,
         sample,
         dem.what_is_your_current_employment_status
         ) %>% 
  add_numeric(exclude = exclude_cols_numeric)
# Inspect colnames
colnames(glad_dat_id)
```


```{r GLAD Look at number of people excluded}
# Inspect dimensions
glad_dat_id %>% 
  dim()
#Differences
glad_excluded <- dim(glad_dat)[1]-dim(glad_dat_id)[1]
glad_excluded
```

Inspect numeric variables
Add summary table with questions as columns, factor levels as rows, with absolute frequencies
```{r GLAD inspect numeric variables}
glad_dat_id %>%
  select(
    all_of(
      ends_with("numeric")
      )
    ) %>%
  freq()
```

Check missingness by missmap
Save all plots at end of script into one object
```{r GLAD inspect missingness}
glad_miss_map <- glad_dat_id %>% 
  missmap()
glad_miss_map
```


## EDGI data
Note: this is an optional questionnaire in EDGI.
```{r EDGI data}
edgi_dat <- readRDS(
  file = paste0(ilovedata,"/data_raw/2022-09-16/edgi/dem_edgi.rds")
  )
#Check
edgi_dat %>%
  colnames()
edgi_dat %>%
  dim()
```

```{r EDGI Select & rename relevant columns}
edgi_dat_id <- edgi_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference,
           .keep_all = TRUE) %>% 
  add_column(sample = "EDGI",
             .after = "externalDataReference") %>% #create new column 
  select(
         ID = externalDataReference, # ID
         startDate,
         endDate,
         sample,
         dem.what_is_your_current_employment_status,
         ) %>% 
  add_numeric(exclude = exclude_cols_numeric)
# Inspect colnames
colnames(edgi_dat_id)
```

```{r EDGI Look at number of people excluded}
# Inspect dimensions
dim(edgi_dat_id)
#Differences
edgi_excluded <- dim(edgi_dat)[1]-dim(edgi_dat_id)[1]
edgi_excluded
```
`edgi.excluded` EDGI participants excluded due to missing data

Inspect numeric variables
Add summary table with questions as columns, factor levels as rows, with absolute frequencies
```{r EDGI inspect numeric variables}
edgi_dat_id %>%
  select(
    all_of(
      ends_with("numeric")
      )
    ) %>%
  freq()
```

Check missingness by missmap
Save all plots at end of script into one object
```{r EDGI inspect missingness}
edgi_miss_map <- edgi_dat_id %>% 
  missmap()
edgi_miss_map
```

Look at difference in names between GLAD and EDGI
```{r Look at difference in names between GLAD and EDGI}
setdiff(colnames(glad_dat_id), colnames(edgi_dat_id))
```

### Change the EDGI variables to match GLAD

```{r change EDGI variables to match GLAD}

edgi_dat_id <- edgi_dat_id %>%
  mutate(
    dem.what_is_your_current_employment_status_numeric = 
      case_when(
        dem.what_is_your_current_employment_status_numeric == 1 ~ 1,
        dem.what_is_your_current_employment_status_numeric == 2 ~ 2,
        dem.what_is_your_current_employment_status_numeric == 3 ~ 3,
        dem.what_is_your_current_employment_status_numeric == 4 ~ 4,
        dem.what_is_your_current_employment_status_numeric == 5 ~ 5,
        dem.what_is_your_current_employment_status_numeric == 6 ~ 6,
        dem.what_is_your_current_employment_status_numeric == 7 ~ 7,
        dem.what_is_your_current_employment_status_numeric == 8 ~ 8,
        dem.what_is_your_current_employment_status_numeric == 9 ~ 9,
        dem.what_is_your_current_employment_status_numeric == 10 ~ 10
      )
  )

edgi_dat_id <- edgi_dat_id %>%
  mutate(
    dem.what_is_your_current_employment_status =
      recode_factor(dem.what_is_your_current_employment_status_numeric,
                    "1" = "Prefer not to answer",
                    "2" = "Seen but not answered",
                    "3" = "In paid employment or self-employed",
                    "4" = "Retired",
                    "5" = "Looking after home and/or family",
                    "6" = "Unable to work because of sickness or disability",
                    "7" = "Unemployed",
                    "8" = "Doing unpaid or voluntary work",
                    "9" = "Full or part-time student",
                    "10" = "None of the above",
                    missing = NA_character_
      )
  )
```

# Bind rows of EDGI and GLAD data
Read in data, bind datasets, then clean all together
```{r Merge data sets}
dat <- glad_dat_id %>%
  bind_rows(edgi_dat_id
            )
#Check
dat %>%
  glimpse()
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```


Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create vector of categorical values for  variables
```{r  vector categorical values}
values_categorical_n_d <- c(
  "In paid employment or self-employed",
  "Retired",
  "Looking after home and/or family",
  "Unable to work because of sickness or disability",
  "Unemployed",
  "Doing unpaid or voluntary work",
  "Full or part-time student",
  "None of the above",
  "Prefer not to answer",
  NA
  )
values_categorical_n_d
```

Create vector of variable names for categorical  variables
```{r  vector categorical variables}
variables_categorical_n_d <-
  c(
    "dem.what_is_your_current_employment_status"
    )
variables_categorical_n_d
```

Use imp_check function to find if any implausible values and obtain summary
table of variables
```{r imp_check categorical variables}
imp_check(data = dat,
          variables = variables_categorical_n_d,
          values = values_categorical_n_d)
```

# Save cleaned data

Check colnames before exporting final dataset
```{r check colnames}
colnames(dat)
```

Combined object for excluded participants
```{r GLAD EDGI save excluded participants}
glad_edgi_excluded <- as.data.frame(rbind(glad_excluded, edgi_excluded))
colnames(glad_edgi_excluded) <- c("Number of Participants Excluded")
rownames(glad_edgi_excluded) <- c("GLAD", "EDGI")
glad_edgi_excluded
```

# GLAD
```{r Write cleaned GLAD variables to a .rds file}
dat %>% 
  filter(sample == "GLAD") %>%  # select only GLAD participants
  saveRDS(
    file = paste0(ilovedata, "/data/2022-09-16/glad/demographics/employment_glad_clean.rds")
    )
```

# EDGI
```{r Write cleaned EDGI variables to a .rds file}
dat %>% 
  filter(sample == "EDGI") %>%  # select only EDGI participants
  saveRDS(
    file = paste0(ilovedata,"/EDGI_protocol/data/demographics/employment_edgi_clean.rds")
    )
```
