---
title: "Data cleaning ethnicity variables in GLAD & EDGI"
author: "Jessica Mundy"
date: "02/06/2021"
output: html_document
---

# Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

```{r Clear global environment}
rm(list=ls())
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in paths file}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovedata_scripts, "functions/add_numeric.R"))
source(file = paste0(ilovedata_scripts, "functions/remove_duplicates.R"))
source(file = paste0(ilovedata_scripts, "functions/sumscores.R"))
source(file = paste0(ilovedata_scripts, "functions/package_check.R"))
source(file = paste0(ilovedata_scripts, "functions/imp_check.R"))
source(file = paste0(ilovedata_scripts, "functions/recode_check.R"))
```
Note: always load tidyverse last
```{r Install load dependencies}
packages = c(
  "summarytools",
  "sjlabelled",
  "Amelia",
  "knitr",
  "gtsummary",
  "tidyverse"
  )
package_check(packages)
```

```{r Get system date}
date <- Sys.Date()
date
```

# Read in the data 

## GLAD data
```{r GLAD data}
glad_dat <- read_rds(
  file = paste0(
    ilovedata, "/data_raw/2022-09-16/glad/dem_glad.rds")
  )
  
# check
glad_dat %>%
  colnames()

glad_dat %>%
  dim()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
```{r GLAD Specify columns to be excluded from add_numeric function}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate"
  )
```

## Select & rename relevant columns (will be a function at some point)
```{r GLAD Select and rename relevant GLAD columns}
glad_dat_id <- glad_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "GLAD",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         dem.what_is_your_ethnic_origin = dem.questions_based_details_gather,
         dem.what_is_your_ethnic_origin.txt = dem.questions_based_details_gather.txt  
         
         # # white ethnic origin
         # dem.white_british = dem.british,                                             
         # dem.white_irish = dem.irish,                                              
         # dem.white_gypsytraveller = dem.gypsytraveller,                                      
         # dem.white_spanish = dem.spanish,                                            
         # dem.white_polish = dem.polish,                                              
         # dem.white_german = dem.german,                                             
         # dem.white_french = dem.french,                                              
         # dem.white_italian = dem.italian,                                            
         # dem.white_other_european = dem.other_european,                                      
         # dem.white_other_europeantext.txt = dem.other_europeantext.txt,                             
         # dem.white_other = dem.other,                                               
         # dem.white_othertext.txt = dem.othertext.txt,                                      
         # dem.white_prefer_not_to_answer = dem.prefer_not_to_answer,    
         # 
         # # black or black british ethnic origin
         # dem.black_caribbean,                                          
         # dem.black_south_african,                                       
         # dem.black_kenyan,                                             
         # dem.black_nigerian,                                            
         # dem.black_ghanaian,                                           
         # dem.black_ugandan,                                             
         # dem.black_other.1,                                            
         # dem.black_othertext.txt.1,                                     
         # dem.black_prefer_not_to_answer.1,                            
         # 
         # # asian or asian british ethnic origin
         # dem.asian_indian,                                              
         # dem.asian_pakistani,                                          
         # dem.asian_chinese,                                             
         # dem.asian_bangladeshi,                                        
         # dem.asian_sri_lanka,                                           
         # dem.asian_iranian,                                            
         # dem.asian_other.2,                                             
         # dem.asian_othertext.txt.2,                                    
         # dem.asian_prefer_not_to_answer.2
        ) %>%
   add_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
glad_dat_id %>% 
  colnames()


# rename .txt variable without "_numeric"
glad_dat_id <- glad_dat_id %>% 
  select(-dem.what_is_your_ethnic_origin.txt) %>%  # get rid of old variable (useless - all NAs)
  rename(dem.what_is_your_ethnic_origin.txt = dem.what_is_your_ethnic_origin.txt_numeric) # rename without "_numeric"

glad_dat_id %>% 
  colnames()
```
                             
```{r GLAD number excluded}
# Inspect dimensions
dim(glad_dat_id)
# Differences
glad_excluded <- dim(glad_dat_id)[1]-dim(glad_dat)[1]
glad_excluded
```
`glad_excluded` GLAD participants excluded due to missing data

### Inspect numeric variables
```{r GLAD inspect numeric variables}
glad_dat_id %>%
  select(all_of(ends_with("numeric"))) %>%
  tbl_summary(missing_text = "Missing")
```

Check missingness by missmap
```{r GLAD inspect missingness}
glad_miss_map <- glad_dat_id %>% 
  missmap()
glad_miss_map
```


## EDGI data
```{r EDGI Read in data}
edgi_dat <- read_rds(
  file = paste0(ilovedata, "/data_raw/2022-09-16/edgi/dem_edgi.rds")
  )
  
# check
edgi_dat %>%
  colnames()
edgi_dat %>%
  dim()
```

### Select and rename relevant columns
```{r EDGI Select and rename relevant columns}
edgi_dat_id <- edgi_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "EDGI",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         startDate,
         endDate,
         sample,
         dem.what_is_your_ethnic_origin = dem.what_is_your_ethnic_origin, 
         dem.what_is_your_ethnic_origin.txt = dem.what_is_your_ethnic_origin.txt   
         
         # white ethnic origin
         # dem.white_british,                                                      
         # dem.white_irish,                                                       
         # dem.white_gypsytraveller,                                              
         # dem.white_spanish,                                                     
         # dem.white_polish,                                                      
         # dem.white_german,                                                      
         # dem.white_french,                                                      
         # dem.white_italian,                                                     
         # dem.white_other_white = demographics.other_white,                                        
         # dem.white_australian = demographics.australian,                                         
         # dem.white_american = demographics.american,                                           
         # dem.white_other = dem.other,                                                       
         # dem.white_othertext.txt = dem.other_text.txt,     # renamed to match GLAD                                         
         # dem.white_prefer_not_to_answer = demographics.prefer_not_to_say,   # renamed to match GLAD   
         # 
         # # mixed ethnic origin
         # dem.mixed_white,                                                       
         # dem.mixed_south_asian,                                                 
         # dem.mixed_east_asian,                                                  
         # dem.mixed_black_african,                                               
         # dem.mixed_black_caribbean,                                             
         # dem.mixed_click_to_write_choice_9 = demographics.click_to_write_choice_9,                            
         # dem.mixed_arab = dem.arab,                                                        
         # dem.mixed_other_mixed = demographics.other_mixed,                                        
         # dem.mixed_other_mixed_text.txt = demographics.other_mixed_text.txt,                               
         # dem.mixed_prefer_not_to_say.1 = demographics.prefer_not_to_say.1,                                
         # 
         # # black or black british ethnic origin
         # dem.black_caribbean,                                                   
         # dem.black_south_african,                                               
         # dem.black_kenyan,                                                      
         # dem.black_nigerian,                                                    
         # dem.black_ghanaian,                                                    
         # dem.black_ugandan,                                                     
         # dem.black_other = demographics.other_black,           # renamed to match GLAD                             
         # dem.black_othertext.txt = demographics.other_black_text.txt,   # renamed to match GLAD                            
         # dem.black_prefer_not_to_answer.1 = dem.prefer_not_to_answer # renamed to match GLAD
         ) %>%
   add_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
edgi_dat_id %>% 
  colnames()

# rename .txt variable without "_numeric"
edgi_dat_id <- edgi_dat_id %>% 
  select(-dem.what_is_your_ethnic_origin.txt) %>%  # get rid of old variable (useless - all NAs)
  rename(dem.what_is_your_ethnic_origin.txt = dem.what_is_your_ethnic_origin.txt_numeric) # rename without "_numeric"

edgi_dat_id %>% 
  colnames()
```

```{r EDGI number excluded}
# Inspect dimensions
dim(edgi_dat_id)
# Differences
edgi_excluded <- dim(edgi_dat_id)[1]-dim(edgi_dat)[1]
edgi_excluded
```
`edgi_excluded` EDGI participants excluded due to missing data

### Inspect numeric variables
```{r EDGI inspect numeric variables}
edgi_dat_id %>%
  select(all_of(ends_with("numeric"))) %>%
  tbl_summary(missing_text = "Missing")
```

Check missingness by missmap
Save all plots at end of script into one object
```{r EDGI inspect missingness}
edgi_miss_map <- edgi_dat_id %>% 
  missmap()
edgi_miss_map
```


## Bind rows of EDGI and GLAD data
Read in data, bind datasets, then clean all together
```{r Merge data sets}
dat <- glad_dat_id %>%
  bind_rows(edgi_dat_id)
#Check
dat %>% glimpse()
```


# Data cleaning

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
```{r Recode NA values}
dat <- dat %>%
   mutate(
     across(
       ends_with("numeric"),
             ~case_when(
             . == -55 ~ -555,   
             . == -77 ~ -777,
             . == -88 ~ -888,
             . == -99 ~ -999,
             TRUE ~ .)
   )
   )
```


## Numeric variables

### Vector of numeric variables for cleaning
```{r Vector of numeric variables for cleaning}
variables_numeric <- c(
  "dem.what_is_your_ethnic_origin_numeric"
)
```

### Vector of plausible numeric values
```{r Vector of plausible numeric values}
values_numeric <- c(
  1,
  2,
  3,
  4,
  5,
  6,
  -888,
  -999,
  NA
)
```

### imp_check numeric values
```{r imp_check numeric values}
imp_check(data = dat,
          variables = variables_numeric,
          values = values_numeric)
```
## Non-numeric values

### Vector of variables for cleaning
```{r Vector of variables for cleaning}
variables <- c(
  "dem.what_is_your_ethnic_origin"
)
```

### Vector of plausible values
```{r Vector of plausible values}
values <- c(
 "White",
 "Mixed",
 "Asian or Asian British",
 "Black or Black British",
 "Arab",
 "Other",
 "Don't know",
 "Prefer not to say",
 NA
)
```

### imp_check values
```{r imp_check values}
imp_check(data = dat,
          variables = variables,
          values = values)
```

# Save cleaned data

## Save variables for export
```{r Save variables for export}
export_variables <- dat %>% 
  select(ID,
         startDate,
         endDate,
         sample,
         dem.what_is_your_ethnic_origin,         
         dem.what_is_your_ethnic_origin.txt,    
         dem.what_is_your_ethnic_origin_numeric) %>% 
  colnames()
```

### GLAD
```{r Write cleaned GLAD variables to a .rds file}
dat %>% 
  filter(sample == "GLAD") %>%  # select only GLAD participants
  select(all_of(export_variables)) %>% 
  saveRDS(
    file = paste0(ilovedata, "/data/2022-09-16/glad/demographics/ethnicity_glad_clean.rds")
    )
```

### EDGI

```{r Write cleaned EDGI variables to a .rds file}
dat %>% 
  filter(sample == "EDGI") %>%  # select only EDGI participants
  select(all_of(export_variables)) %>% 
  saveRDS(
    file = paste0(ilovedata, "/EDGI_protocol/data/demographics/ethnicity_edgi_clean.rds")
    )
```

### GLAD EDGI
```{r Write cleaned GLAD & EDGI variables to a .rds file}
dat %>% 
  select(all_of(export_variables)) %>% 
  saveRDS(
    file = paste0(ilovedata, "/data/2022-09-16/glad_edgi/demographics/ethnicity_glad_edgi_clean.rds")
    )
```

