---
title: "Gender Transgender Sexuality"
author: "Shannon Bristow"
date: '2022-09-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "Gender, transgender and sexuality"
author: "Alicia Peel"
date: "09/06/2021"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
 source(file = "scripts/functions/add_numeric.R")
 source(file = "scripts/functions/remove_duplicates.R")
 source(file = "scripts/functions/sumscores.R")
 source(file = "scripts/functions/package_check.R")
 source(file = "scripts/functions/imp_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c(
  "summarytools", 
  "sjlabelled", 
  "Amelia", 
  "gtsummary", 
  "tidyverse"
  )
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

Read in file with path to ilovedata channel on Teams
```{r Read in file with path to ilovedata channel on teams}
source(file = "../credentials/paths.R")
```

# Read in the data: Demographics

## GLAD data
```{r GLAD read in data}
glad_dat <- readRDS(
  file = paste0(ilovedata, "/data_raw/2022-09-16/glad/dem_glad.rds")
  )
  
# Check variable names in dataframe
glad_dat %>%
  colnames()
# Inspect dimensions of dataframe 
glad_dat %>%
  dim()
```

Specify columns to be excluded from add_numeric function
```{r GLAD specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate"
  )
```

Select & rename relevant columns
```{r GLAD select}
glad_dat_id <- glad_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "GLAD", 
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         dem.sex = dem.select_questionnaire_items_medical,
         dem.which_gender_do_you_identify_with,
         dem.do_you_identify_as_transgender,
         dem.what_is_your_sexual_orientation
         ) %>%
  add_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
glad_dat_id %>%
  colnames()
```

Look at number of people excluded
```{r GLAD number excluded}
# Inspect dimensions of new data set
glad_dat_id %>%
  dim()

# Inspect number of rows dropped
glad_excluded <- dim(glad_dat_id)[1] - dim(glad_dat)[1]
glad_excluded
```

Inspect numeric variables
```{r GLAD inspect numeric variables}
glad_dat_id %>%
  select(all_of(ends_with("numeric"))) %>%
  tbl_summary(missing_text = "Missing")
```

Check missingness by missmap
```{r GLAD inspect missingness}
 glad_miss_map <- glad_dat_id %>% 
   missmap()

 glad_miss_map
```

## EDGI data
```{r EDGI read in data}
edgi_dat <- readRDS(
  file = paste0(ilovedata, "/data_raw/2022-09-16/edgi/dem_edgi.rds")
  )
  
# Check variable names in dataframe
edgi_dat %>%
  colnames()
# Inspect dimensions of dataframe 
edgi_dat %>%
  dim()
```

Find differences between colnames of GLAD and EDGI dataframes
```{r Check colnames}
setdiff(colnames(glad_dat), colnames(edgi_dat))
```

Select & rename relevant columns (will be a function at some point)
```{r EDGI select}
edgi_dat_id <- edgi_dat %>% # New dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "EDGI", 
             .after = "externalDataReference") %>% # Create new sample column 
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate, 
         dem.sex = dem.select_questionnaire_items_relevant,
         dem.what_gender_do_you_identify_with,
         dem.do_you_identify_as_transgender = dem.do_you_consider_yourself_to_be_transgender,
         dem.what_is_your_sexual_orientation
         ) %>%
  add_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
edgi_dat_id %>%
  colnames()
```

Look at number of people excluded
```{r EDGI number excluded}
# Inspect dimensions of new data set
edgi_dat_id %>%
  dim()

# Inspect number of rows dropped
edgi_excluded <- dim(edgi_dat_id)[1] - dim(edgi_dat)[1]
edgi_excluded
```

Inspect numeric variables
```{r EDGI inspect numeric variables}
edgi_dat_id %>%
  select(all_of(ends_with("numeric"))) %>%
   tbl_summary(missing_text = "Missing")
```

Check missingness by missmap
```{r EDGI inspect missingness}
 edgi_miss_map <- edgi_dat_id %>% 
   missmap()
edgi_miss_map
```

# Bind rows of EDGI and GLAD data
Read in data, bind datasets, then clean all together
```{r Merge data sets}
dat <- glad_dat_id %>%
  bind_rows(edgi_dat_id)
#Check
dat %>% glimpse()
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```

# Numeric 0-1 variables

Cleaning numeric variables
```{r vector of numeric values}
values_numeric_0_1 <- c(
  0,
  1,
  -777,
  NA
  )
values_numeric_0_1
```

Create vector of variable names for numeric variables
```{r vector numeric variables}
variables_numeric_0_1 <- c(
    "dem.sex_numeric",
    "dem.do_you_identify_as_transgender_numeric"
  )
variables_numeric_0_1
```

Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check numeric variables}
imp_check(data = dat,
           variables = variables_numeric_0_1,
          values = values_numeric_0_1)
```

# Numeric 0-3 variables

Cleaning numeric variables
```{r vector of numeric values}
values_numeric_0_3 <- c(
  0,
  1,
  2,
  3,
  -888,
  -999,
  NA
  )
values_numeric_0_3
```

Vector of numeric variables
```{r numeric variables vector}
variables_numeric_0_3 <- c(
    "dem.which_gender_do_you_identify_with_numeric"
  )
variables_numeric_0_3
```

Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check numeric variables}
imp_check(data = dat,
           variables = variables_numeric_0_3,
          values = values_numeric_0_3)
```

# Numeric 1-5 variables

Create vector of numeric values 
```{r vector of numeric values}
values_numeric_1_5 <- c(
  1,
  2,
  3,
  4,
  5,
  -999,
  NA
  )
values_numeric_1_5
```

Vector of numeric variables
```{r numeric variables vector}
variables_numeric_1_5 <- c(
    "dem.what_is_your_sexual_orientation_numeric"
  )
variables_numeric_1_5
```

Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check numeric variables}
imp_check(data = dat,
           variables = variables_numeric_1_5,
          values = values_numeric_1_5)
```

# Categorical 0-1 variables (sex)

Create vector of categorical values for variables
```{r vector of categorical labels}
values_categorical_sex <- c(
  "Male",
  "Female",
  "Seen but not answered",
  NA
  )
values_categorical_sex
```

Create vector of variable names
```{r vector categorical variables}
variables_categorical_sex <- c(
    "dem.sex"
  )
variables_categorical_sex
```

Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check categorical variables}
imp_check(data = dat,
           variables = variables_categorical_sex,
          values = values_categorical_sex)
```

# Categorical 0-1 variables (transgender)

Create vector of categorical values for variables
```{r vector of categorical labels}
values_categorical_trans <- c(
  "No",
  "Yes",
  "Seen but not answered",
  NA
  )
values_categorical_trans
```

Create vector of variable names
```{r vector categorical variables}
variables_categorical_trans <- c(
    "dem.do_you_identify_as_transgender"
  )
variables_categorical_trans
```

Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check categorical variables}
imp_check(data = dat,
           variables = variables_categorical_trans,
          values = values_categorical_trans)
```

# Categorical 0-3 variables

Create vector of categorical values for variables
```{r vector of categorical labels}
values_categorical_0_3 <- c(
  "Male",
  "Female",
  "Non-binary",
  "Self-define",
  "Seen but not answered",
  "Don't know",
  "Prefer not to answer",
  NA
  )
values_categorical_0_3
```

Create vector of variable names
```{r vector categorical variables}
variables_categorical_0_3 <- c(
    "dem.which_gender_do_you_identify_with"
  )
variables_categorical_0_3
```

Use imp_check function to find if any implausible values and obtain summary table of variables 
```{r imp_check categorical variables}
imp_check(data = dat,
           variables = variables_categorical_0_3,
          values = values_categorical_0_3)
```

Remove once cleaned on Qualtrics
```{r Recode incorrect categorical variables}
dat <- dat %>%
  mutate(
    across(all_of(variables_categorical_0_3), 
           .fns = ~dplyr::recode(.,
             "self-define" = "Self-define"
            )
          )
  )
```

```{r Check correction applied}
dat %>%
  select(all_of(variables_categorical_0_3)) %>%
  freq()
```

# Categorical 1-5 variables

Create vector of categorical values for variables
```{r vector of categorical labels}
values_categorical_1_5 <- c(
  "Heterosexual",
  "Homosexual",
  "Bisexual",
  "Asexual",
  "Self-define",
  "Other",
  "Seen but not answered",
  "Don't know",
  "Prefer not to answer",
  NA
  )
values_categorical_1_5
```

Create vector of variable names
```{r vector categorical variables}
variables_categorical_1_5 <- c(
    "dem.what_is_your_sexual_orientation"
  )
variables_categorical_1_5
```

Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check categorical variables}
imp_check(data = dat,
           variables = variables_categorical_1_5,
          values = values_categorical_1_5)
```

Remove once cleaned on Qualtrics
```{r Recode incorrect categorical variables}
dat <- dat %>%
  mutate(
    across(all_of(variables_categorical_1_5), 
           .fns = ~dplyr::recode(.,
             "Prefer not to say" = "Prefer not to answer"
            )
          )
  )
```

```{r Check correction applied}
dat %>%
  select(all_of(variables_categorical_1_5)) %>%
  freq()
```

# Save cleaned data

Check colnames before exporting final dataset
```{r check colnames}
colnames(dat)
```

Combined object for excluded participants
```{r GLAD EDGI save excluded participants}
glad_edgi_excluded <- as.data.frame(rbind(glad_excluded, edgi_excluded))
colnames(glad_edgi_excluded) <- c("Number of Participants Excluded")
rownames(glad_edgi_excluded) <- c("GLAD", "EDGI")
glad_edgi_excluded
```

# GLAD
```{r Write cleaned GLAD variables to a .rds file}
dat %>% 
  filter(sample == "GLAD") %>%  # select only GLAD participants
  saveRDS(
    file = paste0(ilovedata, "/data/2022-09-16/glad/demographics/sex_gender_sexuality_glad_clean.rds")
    )
```

# EDGI
```{r Write cleaned EDGI variables to a .rds file}
dat %>% 
  filter(sample == "EDGI") %>%  # select only EDGI participants
  saveRDS(
    file = paste0(ilovedata, "/EDGI_protocol/data/demographics/sex_gender_sexuality_edgi_clean.rds")
    )
```

# GLAD EDGI
```{r Write cleaned GLAD & EDGI variables to a .rds file}
dat %>% 
  filter(sample == "GLAD"
         | sample == "EDGI") %>%  # select only GLAD or EDGI participants
  saveRDS(
    file = paste0(ilovedata, "/data/2022-09-16/glad_edgi/demographics/sex_gender_sexuality_glad_edgi_clean.rds")
    )
```