---
title: "Highest_education_SB"
author: "Shannon Bristow"
date: '2022-09-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "Cleaning education variables and deriving highest education variable in GLAD & EDGI"
author: "Chelsea Mika Malouf"
date: "29/07/2021"
output: html_document
---

This is the cleaning script for the education variables in GLAD & EDGI and the chunks of code to create a derived variable for "highest education". 
Please note that the numeric variables contain -777, but for some reason these are dropped in the non-numeric versions (i.e., the non-numeric versions do not have "Seen but not answered" in them.)

# Set up 
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
)
```

```{r Delete everything in your global environment}
remove(list = ls())
```

```{r Read in functions}
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/imp_check.R")
source(file = "scripts/functions/add_numeric.R")
```

```{r Install load dependencies}
packages <- c("summarytools",
              "sjlabelled",
              "Amelia",
              "gtsummary",
              "tidyverse")

package_check(packages)
```

```{r Recent date}
date <- Sys.Date()
date
```

```{r Read in file with path to ilovedata channel on teams}
source(file = "../credentials/paths.R")
```


# Read in the data

## GLAD data
```{r GLAD read in data}
glad_dat <- read_rds(
  file = paste0(ilovedata, "/data_raw/2022-09-16/glad/dem_glad.rds")
  )
  
# Check variable names in dataframe
glad_dat %>%
  colnames()

# Inspect dimensions of dataframe 
glad_dat %>%
  dim()
```

```{r GLAD specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate"
  )
```

Select & rename relevant columns
```{r GLAD select}
glad_dat_id <- glad_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  distinct(externalDataReference, .keep_all = TRUE) %>% # Keeps only the first line of the duplicates
  add_column(sample = "GLAD",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         dem.college_or_university_degree, #Which of the qualifications do you have?
         dem.a_levelsas_levels_or_equivalent , #Which of the qualifications do you have?
         dem.o_levelsgcses_or_equivalent , #Which of the qualifications do you have?
         dem.cses_or_equivalent , #Which of the qualifications do you have?
         dem.nvq_or_hnd_or_hnc_or_equivalent , #Which of the qualifications do you have?
         dem.other_professional_qualifications , #Which of the qualifications do you have?
         dem.none_of_the_above #Which of the qualifications do you have?# other columns as necessary
         )%>%
  add_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
glad_dat_id %>%
  colnames()
```

Look at number of people excluded
```{r GLAD number excluded}
# Inspect dimensions of new data set
glad_dat_id %>%
  dim()

# Inspect number of rows dropped
glad_excluded <- dim(glad_dat_id)[1] - dim(glad_dat)[1]
glad_excluded
```

Check missingness by missmap
```{r GLAD inspect missingness}
glad_miss_map <- glad_dat_id %>% 
  missmap()

glad_miss_map
```

## EDGI demographics data
```{r EDGI Read in data}
edgi_dat <- read_rds(
  file = paste0(ilovedata, "/data_raw/2022-09-16/edgi/dem_edgi.rds")
  )
  
# Check variable names in dataframe
edgi_dat %>%
  colnames()

# Inspect dimensions of dataframe 
edgi_dat %>%
  dim()

```

Find differences between colnames of GLAD and EDGI dataframes
`setdiff()` gives the items in the first argument that are not in the second argument
```{r Check colnames}
setdiff(colnames(edgi_dat), colnames(glad_dat))
```

Select & rename relevant columns
```{r EDGI select & rename relevant columns}
edgi_dat_id <- edgi_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  distinct(externalDataReference, .keep_all = TRUE) %>% # Keeps only the first line of the duplicates
  add_column(sample = "EDGI",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         dem.college_or_university_degree, 
         dem.a_levelsas_levels_or_equivalent,
         dem.o_levelsgcses_or_equivalent, 
         dem.cses_or_equivalent,
         dem.nvq_or_hnd_or_hnc_or_equivalent,
         dem.other_professional_qualifications,
         dem.none_of_the_above
         ) %>%
  add_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
edgi_dat_id %>%
  colnames()
```

Look at number of people excluded
```{r EDGI number excluded}
# Inspect dimensions
dim(edgi_dat_id)

#Differences 
edgi_excluded <- dim(edgi_dat_id)[1]-dim(edgi_dat)[1]
edgi_excluded
```

Check missingness by missmap
```{r EDGI inspect missingness}
edgi_miss_map <- edgi_dat_id %>% 
  missmap()

edgi_miss_map
```

# Bind rows of GLAD & EDGI
```{r Merge data sets}
dat <- glad_dat_id %>%
  bind_rows(edgi_dat_id)

# Check
dat %>% glimpse()
```


# Data cleaning 

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```


# Numeric variables

The following variables are coded 0 for no, 1 for yes (yes/no response)

## Vector of numeric values 
```{r Vector numeric values}
values_numeric_0_1 <- c(
  -777, # only seen but not answered
  0,
  1,
  NA
  )
values_numeric_0_1
```

## Vector of answer options for numeric variables
```{r Vector of answer options for numeric variables}
variables_numeric_0_1 <-
  c(
    "dem.college_or_university_degree_numeric" ,
    "dem.a_levelsas_levels_or_equivalent_numeric" ,
    "dem.o_levelsgcses_or_equivalent_numeric" ,
    "dem.cses_or_equivalent_numeric" ,
    "dem.nvq_or_hnd_or_hnc_or_equivalent_numeric" ,
    "dem.other_professional_qualifications_numeric" ,
    "dem.none_of_the_above_numeric"
    )
variables_numeric_0_1
```


```{r imp_check numeric variables}
imp_check(data = dat,
          variables = variables_numeric_0_1,
          values = values_numeric_0_1)
```

# Non-numeric variables 

## Vector of variable name for Uni/College
```{r Vector of variable name for Uni/College}
variables_categorical_0_1_uni <-
  c(
    "dem.college_or_university_degree"
    )
variables_categorical_0_1_uni
```

## Vector of answer options for University or College degree
```{r Vector of answer options for University or College degree}
values_categorical_0_1_uni <- 
  c(
  "Not College or university degree" ,
  "College or university degree" ,
  NA
  )
values_categorical_0_1_uni
```

## Imp_check variable University or College degree
```{r imp_check variable University or College degree}
imp_check(data = dat,
          variables = variables_categorical_0_1_uni,
          values = values_categorical_0_1_uni)

#++Variable names for EDGI do not match GLAD. Need to mutate variable
```

### Making the names the same across EDGI and GLAD College/University. Remove once fixed on Qualtrics
++ EDGI had College/University whereas GLAD had College or university degree. Changed to match GLAD
++ Mika Malouf messaged Molly Davies to change the variables in EDGI to match that of GLAD in Qualtrics. 
```{r Unify labels for University or College degree}
dat <- dat %>%  
  mutate(dem.college_or_university_degree = 
           fct_recode(dem.college_or_university_degree,
    "Not College or university degree" = "Not College/University",
    "College or university degree" = "College/University")
    )
```

## Re do imp_check University or College degree
```{r Re do imp_check University or College degree}
imp_check(data = dat,
          variables = variables_categorical_0_1_uni,
          values = values_categorical_0_1_uni)
```

## Vector of variable name for A levels
```{r Vector of variable name A levels}
variables_categorical_0_1_a_levels <-
  c(
    "dem.a_levelsas_levels_or_equivalent"
    )
variables_categorical_0_1_a_levels
```

## Vector of answer options for A levels
```{r Vector of answer options for A levels}
values_categorical_0_1_a_levels <- 
  c(
  "Not A levels/AS levels or equivalent" ,
  "A levels/AS levels or equivalent" ,
  NA
  )
values_categorical_0_1_a_levels
```

## imp_check A levels
```{r imp_check A levels}
imp_check(data = dat,
          variables = variables_categorical_0_1_a_levels,
          values = values_categorical_0_1_a_levels)
```

###Making the names the same across EDGI and GLAD A levels. Remove once fixed on Qualtrics
Changed to make EDGI match GLAD
++ There were implausible values for all variables, so in this section the variable is recoded to match GLAD. Numeric variables were fine
++ Mika Malouf messaged Molly Davies to change the variables in EDGI to match that of GLAD in Qualtrics. 
```{r unify all labels A levels}
dat <- dat %>%  
  mutate(dem.a_levelsas_levels_or_equivalent = 
           fct_recode(dem.a_levelsas_levels_or_equivalent,
    "Not A levels/AS levels or equivalent" = "Not As/A Levels",
    "A levels/AS levels or equivalent" = "As/A Levels")
    )
```

## Re do imp_check A levels
```{r Re do imp_check A levels}
imp_check(data = dat,
          variables = variables_categorical_0_1_a_levels,
          values = values_categorical_0_1_a_levels)
```

## Vector of variable name for O levels/GCSEs
```{r Vector of variable names O levels/GCSEs}
variables_categorical_0_1_o_levels <-
  c(
    "dem.o_levelsgcses_or_equivalent"
    )
variables_categorical_0_1_o_levels
```

## Vector of answer options for O levels/GCSEs
```{r Vector of answer options for O levels/GCSEs}
values_categorical_0_1_o_levels <-
  c(
    "Not O levels/GCSEs or equivalent" ,
    "O levels/GCSEs or equivalent" ,
    NA
    )
values_categorical_0_1_o_levels
```

## Imp_check O levels/GCSEs
```{r imp_check O levels/GCSEs}
imp_check(data = dat,
          variables = variables_categorical_0_1_o_levels,
          values = values_categorical_0_1_o_levels)

#++EDGI variable does not match GLAD. variable needs to be mutated to match
```

### Making the names the same across EDGI and GLAD GCSE. Remove once fixed on Qualtrics
EDGI codes changed to match GLAD
++ Mika Malouf messaged Molly Davies to change the variables in EDGI to match that of GLAD in Qualtrics. 
```{r Unify all labels O levels/GCSEs}
dat <- dat %>%  
  mutate(dem.o_levelsgcses_or_equivalent = 
           fct_recode(dem.o_levelsgcses_or_equivalent,
    "Not O levels/GCSEs or equivalent" = "Not GCSE",
    "O levels/GCSEs or equivalent" = "GCSE")
    )
```

## Re do imp_check O levels/GCSEs
```{r Re do imp_check O levels/GCSEs}
imp_check(data = dat,
          variables = variables_categorical_0_1_o_levels,
          values = values_categorical_0_1_o_levels)

#++no more implausible values
```

## Vector of variable name for CSES or equivalent
```{r Vector of variables CSEs or equivalent }
variables_categorical_0_1_cses <-
  c(
    "dem.cses_or_equivalent"
    )
variables_categorical_0_1_cses
```

## Vector of answer options for CSES or equivalent 
```{r Vector of answer options for CSES or equivalent }
values_categorical_0_1_cses <-
  c(
    "Not CSEs or equivalent"  ,
    "CSEs or equivalent" ,
    NA
    )
values_categorical_0_1_cses
```

## imp_check CSEs or equivalent
```{r imp_check CSEs or equivalent}
imp_check(data = dat,
          variables = variables_categorical_0_1_cses,
          values = values_categorical_0_1_cses)
#++EDGI variable does not match GLAD. variable needs to be mutated to match
```

### Making the names the same across EDGI and GLAD CSE. Remove once fixed on Qualtrics
EDGI codes changed to match GLAD
++ There were implausible values for all variables, so in this section the variable is recoded to match GLAD. Numeric variables were fine
++ Mika Malouf messaged Molly Davies to change the variables in EDGI to match that of GLAD in Qualtrics. 
```{r unify all labels CSEs or equivalent}
dat <- dat %>%  
  mutate(dem.cses_or_equivalent = 
           fct_recode(dem.cses_or_equivalent,
    "Not CSEs or equivalent" = "Not CSE",
    "CSEs or equivalent" = "CSE")
    )
```

## Re do imp_check CSEs or equivalent
```{r Re do imp_check CSEs or equivalent}
imp_check(data = dat,
          variables = variables_categorical_0_1_cses,
          values = values_categorical_0_1_cses)
```

## Vector of variable name for NVQ or equivalent
```{r Vector of variable name for NVQ or equivalent}
variables_categorical_0_1_nvq <-
  c(
    "dem.nvq_or_hnd_or_hnc_or_equivalent"
    )
variables_categorical_0_1_nvq
```

## Vector of answer options for NVQ or equivalent
```{r Vector of answer options for NVQ or equivalent}
values_categorical_0_1_nvq <-
  c(
    "Not NVQ or HND or HNC or equivalent" ,
    "NVQ or HND or HNC or equivalent" ,
    NA
    )
values_categorical_0_1_nvq
```

## imp_check NVQ or equivalent
```{r imp_check NVQ or equivalent}
imp_check(data = dat,
          variables = variables_categorical_0_1_nvq,
          values = values_categorical_0_1_nvq)
#++EDGI variable does not match GLAD. variable needs to be mutated to match
```

### Making the names the same across EDGI and GLAD NVQ. Remove once fixed on Qualtrics
EDGI codes changed to match GLAD
++ There were implausible values for all variables, so in this section the variable is recoded to match GLAD. Numeric variables were fine
++ Mika Malouf messaged Molly Davies to change the variables in EDGI to match that of GLAD in Qualtrics. 
```{r unify all labels NVQ or equivalent}
dat <- dat %>%  
  mutate(dem.nvq_or_hnd_or_hnc_or_equivalent = 
           fct_recode(dem.nvq_or_hnd_or_hnc_or_equivalent,
    "Not NVQ or HND or HNC or equivalent" = "Not NVQ",
    "NVQ or HND or HNC or equivalent" = "NVQ")
  )
```

## Re do imp_check NVQ or equivalent
```{r Re do imp_check NVQ or equivalent}
imp_check(data = dat,
          variables = variables_categorical_0_1_nvq,
          values = values_categorical_0_1_nvq)
```

## Vector of variable name for Other Professional Qualifications
```{r Vector variable name for Other Professional Qualifications}
variables_categorical_0_1_other <-
  c(
    "dem.other_professional_qualifications"
    )
variables_categorical_0_1_other
```

## Vector of answer options for Other Professional Qualifications
```{r Vector of answer options Other Professional Qualifications}
values_categorical_0_1_other <-
  c(
    "Not Other professional qualifications"  ,
    "Other professional qualifications" ,
    NA
    )
values_categorical_0_1_other
```

## imp_check Other Professional Qualifications
```{r imp_check Other Professional Qualifications}
imp_check(data = dat,
          variables = variables_categorical_0_1_other,
          values = values_categorical_0_1_other)
#++EDGI variable does not match GLAD. variable needs to be mutated to match
```

### Making the names the same across EDGI and GLAD Other qualifications. Remove once fixed on Qualtrics
EDGI codes changed to match GLAD
++ There were implausible values for all variables, so in this section the variable is recoded to match GLAD. Numeric variables were fine
++ Mika Malouf messaged Molly Davies to change the variables in EDGI to match that of GLAD in Qualtrics.
```{r Unify all labels Other Professional Qualifications}
dat <- dat %>%  
  mutate(dem.other_professional_qualifications = 
           fct_recode(dem.other_professional_qualifications,
    "Not Other professional qualifications" = "Not Other",
    "Other professional qualifications" = "Other")
  )
```

## Re do imp_check Other Professional Qualifications
```{r Re do imp_check Other Professional Qualifications}
imp_check(data = dat,
          variables = variables_categorical_0_1_other,
          values = values_categorical_0_1_other)
```


## Vector of variable name for none of the above
```{r Vector of variable name for None of the above}
variables_categorical_0_1_none <-
  c(
    "dem.none_of_the_above"
    )
variables_categorical_0_1_none
```

## Vector of answer options for None the above 
```{r Vector of answer options for None the above e}
values_categorical_0_1_none <-
  c(
    "Not None of the above" ,
    "None of the above" ,
    NA
    )
values_categorical_0_1_none
```

## imp_check None of the above
```{r imp_check None of the above}
imp_check(data = dat,
          variables = variables_categorical_0_1_none,
          values = values_categorical_0_1_none)
#++no implausible values. can leave as is
```


# Make a categorical variable where highest_education is the variable and qualifications are categories - collapsed
dem.highest_education in similar style as PANCHANGE created variable. None of the above category is added.
### This variable is for purpose of merging data with RAMP to allow consistency across datasets
```{r Create highest education collapsed variable}
dat <- dat %>%
  mutate(
    dem.highest_education_collapsed_numeric =
      case_when(
        dem.college_or_university_degree_numeric == "1" ~ 4,
        dem.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
        dem.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
        dem.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
        dem.cses_or_equivalent_numeric == "1" ~ 1,
        dem.none_of_the_above_numeric == "1" ~ 0 )
    )

# recode the numeric version into a factor
dat <- dat %>%
  mutate(
    dem.highest_education_collapsed =
      recode_factor(
        dem.highest_education_collapsed_numeric,
        `0` = "None of the above" ,
        `1` = "GCSEs/CSEs/O-levels or equivalent",
        `2` = "NVQ/HND/HNC or equivalent",
        `3` = "A-levels/AS-levels or equivalent",
        `4` = "University")
    )

dat %>%
  select(dem.highest_education_collapsed,
         dem.highest_education_collapsed_numeric) %>% 
  freq()
```

# Make a categorical variable where highest_education is the variable and qualifications are categories - finegrained
dem.highest_education in similar style as PANCHANGE created variable. None of the above category is added.
```{r Create highest education finegrained variable}
dat <- dat %>%
  mutate(
    dem.highest_education_finegrained_numeric =
      case_when(
        dem.college_or_university_degree_numeric == "1" ~ 5,
        dem.a_levelsas_levels_or_equivalent_numeric == "1" ~ 4,
        dem.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 3,
        dem.o_levelsgcses_or_equivalent_numeric == "1" ~ 2,
        dem.cses_or_equivalent_numeric == "1" ~ 1,
        dem.none_of_the_above_numeric == "1" ~ 0 )
    )

# recode the numeric version into a factor
dat <- dat %>%
  mutate(
    dem.highest_education_finegrained =
      recode_factor(
        dem.highest_education_finegrained_numeric,
        `0` = "None of the above" ,
        `1` = "CSEs or equivalent",
        `2` = "O-levels/GCSEs or equivalent",
        `3` = "NVQ/HND/HNC or equivalent",
        `4` = "AS-levels/A-levels or equivalent",
        `5` = "University degree or equivalent"
        )
    )

dat %>%
  select(dem.highest_education_finegrained,
         dem.highest_education_finegrained_numeric) %>% 
  freq()
```


# Save cleaned data

## Check colnames before exporting final dataset
```{r check colnames}
dat %>% colnames()
```

## Combined object for excluded participants
```{r GLAD EDGI save excluded participants}
glad_edgi_excluded <- as.data.frame(rbind(glad_excluded, edgi_excluded))
colnames(glad_edgi_excluded) <- c("Number of Participants Excluded")
rownames(glad_edgi_excluded) <- c("GLAD", "EDGI")
glad_edgi_excluded
```

## GLAD
```{r Write cleaned GLAD variables to a .rds file}
dat %>% 
  filter(sample == "GLAD") %>%  # select only GLAD participants
  saveRDS(
    file = paste0(ilovedata, "/data/2022-09-16/glad/demographics/highest_education_glad_clean.rds")
    )
```

## EDGI
```{r Write cleaned EDGI variables to a .rds file}
dat %>% 
  filter(sample == "EDGI") %>%  # select only EDGI participants
  saveRDS(
    file = paste0(ilovedata, "/EDGI_protocol/data/demographics/highest_education_edgi_clean.rds")
    )
```

## GLAD & EDGI
```{r Write cleaned GLAD & EDGI variables to a .rds file}
dat %>% 
  filter(sample == "GLAD"
         | sample == "EDGI") %>%  # select only GLAD or EDGI participants
  saveRDS(
    file = paste0(ilovedata, "/data/2022-09-16/glad_edgi/demographics/highest_education_glad_edgi_clean.rds")
    )
```
