---
title: "Marital_status_cleaning"
author: "Steven Bright"
date: "14/09/2021"
output: html_document
---

All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (e.g. GLAD/EDGI/NBR) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in paths file}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovedata_scripts, "functions/add_numeric.R"))
source(file = paste0(ilovedata_scripts, "functions/remove_duplicates.R"))
source(file = paste0(ilovedata_scripts, "functions/sumscores.R"))
source(file = paste0(ilovedata_scripts, "functions/package_check.R"))
source(file = paste0(ilovedata_scripts, "functions/imp_check.R"))
source(file = paste0(ilovedata_scripts, "functions/recode_check.R"))
```


Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```


# Read in the data: What is your current marital/relationship status?
Change this heading to the name of your questionnaire/demographic
Load GLAD data first, then EDGI, then NBR, then RAMP

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (GLAD, EDGI, NBR, RAMP)

## GLAD data

```{r GLAD load data}
glad_dat <- read_rds(
  file = paste0(ilovedata, "/data_raw/2022-09-16/glad/dem_glad.rds")
  )
  
# Check variable names in dataframe
glad_dat %>%
  colnames()

# Inspect dimensions of dataframe 
glad_dat %>%
  dim()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
NB: If this is data from the COPING survey, add "_coping" to the end of each variable name
```{r Specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate"
  )
```

Select & rename relevant columns
```{r GLAD select}
glad_dat_id <- glad_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "GLAD",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         dem.what_is_your_current_maritalrelationship_status
         ) %>%
  add_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
glad_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r GLAD number excluded}
# Inspect dimensions of new data set
glad_dat_id %>%
  dim()

# Inspect number of rows dropped
glad_excluded <- dim(glad_dat_id)[1] - dim(glad_dat)[1]
glad_excluded
```

Inspect numeric variables
```{r GLAD inspect numeric variables}
glad_dat_id %>%
  select(all_of(ends_with("numeric"))) %>%
  tbl_summary(missing_text = "Missing")
```

Check missingness by missmap
@me Save all plots at end of script into one object
```{r GLAD inspect missingness}
glad_miss_map <- glad_dat_id %>% 
  missmap()

glad_miss_map
```

## EDGI data

```{r EDGI load data}
edgi_dat <- read_rds(
  file = paste0(ilovedata, "/data_raw/2022-09-16/edgi/dem_edgi.rds")
  )
  
# Check variable names in dataframe
edgi_dat %>%
  colnames()

# Inspect dimensions of dataframe 
edgi_dat %>%
  dim()
```

Find differences between colnames of GLAD and EDGI dataframes
`setdiff()` gives the items in the first argument that are not in the second argument
```{r Check colnames}
setdiff(colnames(glad_dat), colnames(edgi_dat))
```


Select & rename relevant columns
NB: If this is data from the COPING survey, add "_coping" to the end of each variable name
```{r EDGI select}
edgi_dat_id <- edgi_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "EDGI",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         dem.what_is_your_current_maritalrelationship_status
         ) %>%
  add_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
edgi_dat_id %>%
  colnames()
```

```{r check factor levels of dem.what_is_your_current_maritalrelationship_status}
edgi_dat_id$dem.what_is_your_current_maritalrelationship_status %>% 
  levels()
```

```{r recode dem.what_is_your_current_maritalrelationship_status EDGI factor levels to match GLAD}
edgi_dat_id <- edgi_dat_id %>% 
  mutate(
    dem.what_is_your_current_maritalrelationship_status = recode_factor(
    dem.what_is_your_current_maritalrelationship_status, 
    "Steady not living together" = "Relationship (not living together)", 
    "Steady living together" = "Relationship (living together)", 
    "Married" = "Married/civil partnership"
    )
  )
```

```{r check dem.what_is_your_current_maritalrelationship_status EDGI factor levels}
edgi_dat_id$dem.what_is_your_current_maritalrelationship_status %>% 
  levels()
```

Look at number of people excluded
Create object at the end of the script showing excluded participants per data set
```{r EDGI number excluded}
# Inspect dimensions of new data set
edgi_dat_id %>%
  dim()

# Inspect number of rows dropped
edgi_excluded <- dim(edgi_dat_id)[1] - dim(edgi_dat)[1]
edgi_excluded
```


Inspect numeric variables
+++CH: There is a mistake with this chunk. I have deactivated it for the moment so the script runs through
+++MD: I've checked this also and can't understand why it's happening here, as to all appearance the dataset/variable are exactly the same as in GLAD. The error suggests it's something to do with the variable label, but I can't find anything wrong.
```{r EDGI inspect numeric variables, eval=FALSE, include=FALSE}
edgi_dat_id %>%
  select(all_of(ends_with("numeric"))) %>%
  tbl_summary(missing_text = "Missing")
```

Check missingness by missmap
@me Save all plots at end of script into one object
```{r EDGI inspect missingness}
edgi_miss_map <- edgi_dat_id %>% 
  missmap()

edgi_miss_map
```

# Bind rows of EDGI and GLAD data
Read in data, bind datasets, then clean all together
```{r Merge data sets}
dat <- glad_dat_id %>%
  bind_rows(edgi_dat_id)

#Check
dat %>% 
  glimpse()
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```


# Cleaning Categorical variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create vector of categorical values for variables
```{r vector categorical values}
values_categorical <- c(
  "Prefer not to answer",
  "Seen but not answered",
  "Single",
  "Relationship (not living together)",
  "Relationship (living together)",
  "Married/civil partnership",
  "Separated",
  "Divorced",
  "Widowed",
  "Other",
  NA_real_
  )
values_categorical
```

Create vector of variable names for categorical Never-Daily variables
```{r vector categorical variables}
variables_categorical <-
  c(
    "dem.what_is_your_current_maritalrelationship_status"
    )
variables_categorical
```

Use imp_check function to find if any implausible values and obtain summary
table of variables
```{r imp_check categorical variables}
imp_check(data = dat,
          variables = variables_categorical,
          values = values_categorical)
```

# Numeric variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create vector of numeric values 
```{r vector numeric values}
values_numeric <- c(
  1,
  2,
  3,
  4,
  5,
  6,
  7,
  8,
  -777,
  -999,
  NA_real_
  )
values_numeric
```

Create vector of variable names for numeric variables
```{r vector numeric variables}
variables_numeric <-
  c(
    "dem.what_is_your_current_maritalrelationship_status_numeric"
    )
variables_numeric
```

Use imp_check function to find if any implausible values and obtain summary
table of variables
```{r imp_check numeric variables}
imp_check(data = dat,
          variables = variables_numeric,
          values = values_numeric)
```

# Save cleaned data

Check colnames before exporting final dataset
```{r check colnames}
colnames(dat)
```

Combined object for excluded participants
```{r GLAD EDGI save excluded participants}
glad_edgi_excluded <- as.data.frame(rbind(glad_excluded, edgi_excluded))
colnames(glad_edgi_excluded) <- c("Number of Participants Excluded")
rownames(glad_edgi_excluded) <- c("GLAD", "EDGI")
glad_edgi_excluded
```
```{r}
dat %>% 
  filter(sample == "EDGI") %>%
  filter(is.na(dem.what_is_your_current_maritalrelationship_status))
```

## GLAD

```{r Write cleaned GLAD variables to a .rds file}
dat %>% 
  filter(sample == "GLAD") %>%  # select only GLAD participants
  saveRDS(
    file = paste0(ilovedata, 
                  "/data/2022-09-16/glad/demographics/marital_status_glad_clean.rds")
    )
```

## EDGI

```{r Write cleaned EDGI variables to a .rds file}
dat %>% 
  filter(sample == "EDGI") %>%  # select only EDGI participants
  saveRDS(
    file = paste0(ilovedata,
                  "/EDGI_protocol/data/demographics/marital_status_edgi_clean.rds")
    )
```

## GLAD EDGI

```{r Write cleaned GLAD & EDGI variables to a .rds file}
dat %>% 
  filter(sample == "GLAD"
         | sample == "EDGI") %>%  # select only GLAD or EDGI participants
  saveRDS(
    file = paste0(ilovedata, 
                  "/data/2022-09-16/glad_edgi/demographics/marital_status_glad_edgi_clean.rds")
    )
```
