---
title: "Smoking_pack_per_year"
author: "Shannon Bristow"
date: '2022-09-29'
output: html_document
---

---
title: "Smoking pack per year"
author: "Yuhao Lin"
date: "3/05/2022"
output: html_document
---

This is a cleaning script to create a pack-year variable based on two
smoking questions. Pack-year is defined as pack smoked per day multiply by
number of years of smoking, where a pack is equivalent to 20 cigarettes.

EDGI & GLAD: 
  Question: 
    1. About how many cigarettes do you/did you smoke per day?
    2. How many years have you/did yousmoke?

Note: At some stage, the EDGI & GLAD data sets will be merged (this is
because they *should* have the exact same questions. 

# Set up 
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = NA,
  prompt = FALSE,
  cache = FALSE
)
```

Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```


Install packages
```{r Install packages}
# install.packages("summarytools")
# install.packages("sjlabelled")
# install.packages("tidyverse")
```

Load packages from library
NB: load tidyverse last!
```{r Load packages from library}
library(summarytools)
library(sjlabelled)
library(tidyverse)
```

Retrieve the recent date
```{r Recent date}
date <- Sys.Date()
date
```

# Add the add_numeric function - used to convert character variables into numeric variables.
```{r Read in functions}
source(file = "scripts/functions/add_numeric.R")
```


Read in file with path to ilovedata channel on Teams
#Read in path file
```{r Read in file with path to ilovedata channel on Teams}
source("../credentials/paths.R")
```



# Read in the data 
## GLAD data
```{r GLAD read in data}
glad_dat <- readRDS(file = paste0(ilovedata, "/data_raw/2022-09-16/glad/dem_glad.rds"))

# Check
glad_dat %>%
  colnames()

glad_dat %>% # check number of rows and columns
  dim()
```

Select relevant columns (will be a function at some point)
```{r GLAD select}
exclude_cols_dem <- c(
  "ID",
  "sample"
)

glad_dat.id <- glad_dat %>% # new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs without ID
  distinct(externalDataReference, .keep_all = TRUE) %>% # Keeps only the first line of the duplicates
  add_column(sample = "GLAD", .after = "externalDataReference") %>% # Create new sample column
  select(
    ID = externalDataReference, # ID
    sample, # Sample
    startDate,
    endDate,
    dem.cigarettes_smoke_day_youdid.txt,
    dem.how_many_years_have_youdid_yousmoke.txt
  )


# Inspect colnames
colnames(glad_dat.id)
```

Look at number of people excluded
```{r GLAD number excluded}
# Inspect dimensions
dim(glad_dat.id)

# Differences
glad_excluded <- dim(glad_dat.id)[1] - dim(glad_dat)[1]
glad_excluded
```


## EDGI demographics data
```{r EDGI Read in data}
edgi_dat <- readRDS(
  file = paste0(ilovedata, "/data_raw/2022-09-16/edgi/dem_edgi.rds")
)

# Check
edgi_dat %>%
  colnames()

edgi_dat %>%
  dim()
```

Select & rename relevant columns (will be a function at some point)
```{r EDGI select}
exclude_cols_dem <- c(
  "ID",
  "sample"
)

edgi_dat.id <- edgi_dat %>% # new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs without ID
  distinct(externalDataReference, .keep_all = TRUE) %>% # Keeps only the first line of the duplicates
  add_column(sample = "EDGI", .after = "externalDataReference") %>% # Create new sample column
  select(
    ID = externalDataReference, # ID
    sample, # Sample
    startDate,
    endDate,
    dem.cigarettes_smoke_day_youdid.txt,
    dem.how_many_years_have_youdid_yousmoke.txt = dem.how_many_years_have_youdid_yousmoke.txt
    )


# Inspect colnames
colnames(edgi_dat.id)
```

Look at number of people excluded
```{r EDGI number excluded}
# Inspect dimensions
dim(edgi_dat.id)

# Differences
edgi_excluded <- dim(edgi_dat.id)[1] - dim(edgi_dat)[1]
edgi_excluded
```

Find differences between colnames of GLAD and EDGI dataframes
`setdiff()` gives the items in the first argument that are not in the second argument
```{r Check colnames}
setdiff(colnames(glad_dat.id), colnames(edgi_dat.id))
```

#Merge EDGI & GLAD for cleaning 
EDGI & GLAD have the same age variables so can be merged together for cleaning
*Select final cleaned variables from EDGI & GLAD dataset and rename, ready to merge together.
```{r Merge data sets}
dat_glad_edgi <- glad_dat.id %>%
  rbind(edgi_dat.id)

names(glad_dat.id) <- names(edgi_dat.id)

# Check 
dat_glad_edgi
```

##Recode NA values to 3 digits
```{r Recode NA values to 3 digits}
dat_glad_edgi <- dat_glad_edgi %>%
  mutate(across(
    ends_with(".txt"),
    ~ case_when(
      . == -77 ~ -777,
      . == -88 ~ -888,
      . == -99 ~ -999,
      TRUE ~ .
    )
  ))
```


#Add suffix "unc" for uncleaned data columns
```{r Add unc suffix}
dat_glad_edgi <- dat_glad_edgi %>%
  rename_with(~ paste(.x, "unc", sep = "_"), starts_with("dem"))
dat_glad_edgi
```

# Clean variables: GLAD & EDGI

```{r check values}
dat_glad_edgi %>%
  descr(dem.how_many_years_have_youdid_yousmoke.txt_unc,
    stats = "common"
  )

freq(dat_glad_edgi$dem.how_many_years_have_youdid_yousmoke.txt_unc)

dat_glad_edgi %>%
  descr(dem.cigarettes_smoke_day_youdid.txt_unc,
    stats = "common"
  )
```




```{r Defining limits}
years_of_smoking_limit <- 100
years_of_smoking_lower_limit <- 0

# What should this be?
cigarettes_per_day_limit <- 999
cigarettes_per_day_lower_limit <- 0
```


## Outlier count
```{r outlier count}
dat_glad_edgi %>%
  filter(
      dem.how_many_years_have_youdid_yousmoke.txt_unc > years_of_smoking_limit |
      dem.how_many_years_have_youdid_yousmoke.txt_unc < years_of_smoking_lower_limit |
      dem.cigarettes_smoke_day_youdid.txt_unc > cigarettes_per_day_limit |
      dem.cigarettes_smoke_day_youdid.txt_unc < cigarettes_per_day_lower_limit
  ) %>%
  nrow()
```

# Calculate pack-years

Define as number of packs per day times number of years of smoking. A pack is 20 cigarettes.

```{r calculate pack year}
dat_glad_edgi <- dat_glad_edgi %>%
  mutate(
    dem.pack_year =
      dem.cigarettes_smoke_day_youdid.txt_unc / 20 *
        dem.how_many_years_have_youdid_yousmoke.txt_unc
  )
```

#Recode outliers to -666
```{r Recode outliers to -666 GLAD}
dat_glad_edgi <- dat_glad_edgi %>%
  mutate(
    dem.pack_year =
      if_else(
        dem.how_many_years_have_youdid_yousmoke.txt_unc > years_of_smoking_limit |
          dem.how_many_years_have_youdid_yousmoke.txt_unc < years_of_smoking_lower_limit |
          dem.cigarettes_smoke_day_youdid.txt_unc > cigarettes_per_day_limit |
          dem.cigarettes_smoke_day_youdid.txt_unc < cigarettes_per_day_lower_limit,
        true = -666,
        false = dem.pack_year,
        missing = NA_real_
      )
  )
```


# After recoding to -666
```{r after recoding to -666}

freq(dat_glad_edgi$dem.pack_year)
```



#Save data
Vector for final variables to export
```{r variables to export}
export_variables <-
  c(
    "ID",
    "sample",
    "dem.pack_year"
  )
```


Join datasets together
```{r GLAD columns export}
glad_dat.exp <- dat_glad_edgi %>%
  filter(sample == "GLAD") %>%
  select(all_of(export_variables))
glad_dat.exp
```

```{r EDGI columns export}
edgi_dat.exp <- dat_glad_edgi %>%
  filter(sample == "EDGI") %>%
  select(all_of(export_variables))
edgi_dat.exp
```



```{r GLAD EDGI NBR export}
glad_edgi_dat.exp <- dat_glad_edgi %>%
  filter(sample == "GLAD" | sample == "EDGI") %>%
  select(all_of(export_variables))
glad_edgi_dat.exp
```


Save data
```{r save GLAD, EDGI, GLAD&EDGI data}
saveRDS(
  object =
    glad_edgi_dat.exp,
  file = paste0(ilovedata, "/data/2022-09-16/glad_edgi/demographics/", "Smoking_pack_year_", date, ".rds")
)
saveRDS(
  object =
    glad_dat.exp,
  file = paste0(ilovedata, "/data/2022-09-16/glad/demographics/", "Smoking_pack_year_GLAD_", date, ".rds")
)
saveRDS(
  object =
    edgi_dat.exp,
  file = paste0(ilovedata, "/EDGI_protocol/data/demographics/", "Smoking_pack_year_EDGI_", date, ".rds")
)
```
