---
title: "Years_of_Education"
author: "Chelsea Mika Malouf"
date: "26/07/2021"
output: html_document
---

This is a cleaning script for the variables over years of education in EDGI and GLAD. Please be aware of some differences in the questions and answer options between these studies.

NBR does not have any variables on years of education completed. RAMP had highest level of education but does not count how many years of education they have had.

EDGI & GLAD: General question about ethnic origin followed up with more specific questions
  Question: How many years did you attend school? You can include pre-school, primary school, secondary school, college/sixth-form, university and post-university education.

Note: At some stage, the EDGI & GLAD data sets will be merged (this is because they *should* have the exact same questions. However, due to a data extraction problem, there are some questions missing in both EDGI & GLAD and this means they don't match up exactly. At this stage, I am leaving them as separate data sets.)

# Set up 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

Delete everything in your global environment
```{r Delete everything in your global environment}
remove(list = ls())
```


Install packages
```{r Install packages}
#install.packages("summarytools")
#install.packages("sjlabelled")
#install.packages("tidyverse")
```

Load packages from library
NB: load tidyverse last!
```{r Load packages from library}
library(summarytools)
library(sjlabelled)
library(tidyverse)
```

Retrieve the recent date
```{r Recent date}
date = Sys.Date()
date
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in paths file}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovedata_scripts, "functions/add_numeric.R"))
source(file = paste0(ilovedata_scripts, "functions/remove_duplicates.R"))
source(file = paste0(ilovedata_scripts, "functions/sumscores.R"))
source(file = paste0(ilovedata_scripts, "functions/package_check.R"))
source(file = paste0(ilovedata_scripts, "functions/imp_check.R"))
source(file = paste0(ilovedata_scripts, "functions/recode_check.R"))
```

# Read in the data 
## GLAD data
```{r GLAD read in data}
glad_dat <- readRDS(file = paste0(ilovedata, "/data_raw/2022-09-16/glad/dem_glad.rds")) # update rds file accordingly

#Check
glad_dat %>%
  colnames()

glad_dat %>% #check number of rows and columns
  dim()
```

Select relevant columns (will be a function at some point)
```{r GLAD select}
exclude_cols_dem <- c("ID",
                  "sample")

glad_dat.id <- glad_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs without ID
  distinct(externalDataReference, .keep_all = TRUE) %>% # Keeps only the first line of the duplicates
  add_column(sample = "GLAD", .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference,# ID
         sample, # Sample
         startDate,
         endDate,
         dem.years_schoolplease_include_preschool.txt,# Years in education (different to EDGI)
         dem.how_old_are_you_now.txt, # Age
         ) 
  # add_numeric(exclude = exclude_cols_dem) %>% ## don't add because original columns are not factors
 
 
# Inspect colnames
colnames(glad_dat.id)
```

Look at number of people excluded
```{r GLAD number excluded}
# Inspect dimensions
dim(glad_dat.id)

#Differences
glad_excluded <- dim(glad_dat.id)[1]-dim(glad_dat)[1]
glad_excluded
```
`r glad.years_of_educ.excluded` GLAD participants were excluded due to missing data on years of education items


## EDGI demographics data
```{r EDGI Read in data}
edgi_dat <- readRDS(
  file = paste0(ilovedata, "/data_raw/2022-09-16/edgi/dem_edgi.rds")) 
  
#Check
edgi_dat %>%
  colnames()

edgi_dat %>%
  dim()

```

Select & rename relevant columns (will be a function at some point)
```{r EDGI select}
exclude_cols_dem <- c("ID",
                  "sample")

edgi_dat.id <- edgi_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs without ID
  distinct(externalDataReference, .keep_all = TRUE) %>% # Keeps only the first line of the duplicates
  add_column(sample = "EDGI", .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference,# ID
         sample, # Sample
         startDate,
         endDate,
         dem.years_schoolplease_include_preschool.txt = dem.attend_school_years_include.txt, # Years in education (different to GLAD so it is changed to be the same as the GLAD variable name)
         dem.how_old_are_you_now.txt, # Age. EDGI data dictionary has it as demographics.how_old_are_you_now.txt but the most recent data file has it as dem.how_old_are_you_now.txt so check
         ) 

 
# Inspect colnames
colnames(edgi_dat.id)
```

Look at number of people excluded
```{r EDGI number excluded}
# Inspect dimensions
dim(edgi_dat.id)

#Differences 
edgi_excluded <- dim(edgi_dat.id)[1]-dim(edgi_dat)[1]
edgi_excluded
```
`r edgi.years_of_educ.excluded` EDGI participants were excluded due to missing data on years of education items



#Merge EDGI & GLAD for cleaning 
EDGI & GLAD have the same age variables so can be merged together for cleaning
*Select final cleaned variables from EDGI & GLAD dataset and rename, ready to merge together.
```{r Merge data sets}
dat_glad_edgi <- glad_dat.id %>%
  rbind(edgi_dat.id)

#Check
dat_glad_edgi

freq(dat_glad_edgi$dem.years_schoolplease_include_preschool.txt)
```

##Recode NA values to 3 digits
```{r Recode NA values to 3 digits}
dat_glad_edgi <- dat_glad_edgi %>%
  mutate(across(ends_with(".txt"),
                ~case_when(
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)
                )
         )
```


#Add suffix "unc" for uncleaned data columns
```{r Add unc suffix}
dat_glad_edgi <- dat_glad_edgi %>%
  rename_with( ~ paste(.x, "unc", sep = "_"), starts_with("dem"))
dat_glad_edgi
```



# Clean variables: GLAD & EDGI

```{r check values}
dat_glad_edgi %>%
  descr(dem.years_schoolplease_include_preschool.txt_unc,
        stats = "common")

freq(dat_glad_edgi$dem.years_schoolplease_include_preschool.txt_unc)
```



#Years of education outliers: The oldest person in the world is 117 years. Cannot be triple digits or a negative number.
Students in the UK legally attend school between ages 5 and 16 (recent number). 
Took someone (as of 2005) 89 years and 111 days to earn a bachelors degree.

Set age and years of education limits
```{r Defining limits for years of education and age}
years_of_educ_upper_limit = 88
years_of_educ_lower_limit = 0
Age_uncleaned_lower_limit = 16
Age_uncleaned_upper_limit = 117
# age limits are added so that if person has an age thats an outlier then they shouldnt count when compared against their education
# read in cleaned age once finished. 
# use the age as the limit
```


##Years of education outlier count
```{r Years of education outlier count}
dat_glad_edgi %>%
  filter(
    dem.how_old_are_you_now.txt_unc > Age_uncleaned_upper_limit | # older than the age limit
    dem.how_old_are_you_now.txt_unc < Age_uncleaned_lower_limit | # younger than the age limit
    dem.years_schoolplease_include_preschool.txt_unc > dem.how_old_are_you_now.txt_unc | # if the person has more years of education than their age 
    dem.years_schoolplease_include_preschool.txt_unc > years_of_educ_upper_limit | # older than the limit for years of education
    dem.years_schoolplease_include_preschool.txt_unc < years_of_educ_lower_limit # less than the limit for years of education
    ) %>%
  nrow()
```

#Recode outliers to -666
```{r Years of education Recode outliers to -666 GLAD}
dat_glad_edgi <- dat_glad_edgi %>%
    mutate(
      dem.university_education_attend_school.txt =
        if_else(
            ((dem.years_schoolplease_include_preschool.txt_unc > 0 &
             dem.years_schoolplease_include_preschool.txt_unc > dem.how_old_are_you_now.txt_unc) | # if the person has more years of education than their age 
            (dem.years_schoolplease_include_preschool.txt_unc > 0 & dem.years_schoolplease_include_preschool.txt_unc > years_of_educ_upper_limit) | # older than the limit for years of education
            (dem.years_schoolplease_include_preschool.txt_unc > 0 & dem.years_schoolplease_include_preschool.txt_unc < years_of_educ_lower_limit)), # less than the limit for years of education
          true = -666,
          false = dem.years_schoolplease_include_preschool.txt_unc,
          missing = NA_real_
        )
    )
```


#Years of education after recoding to -666
```{r Years of education after recoding to -666}

freq(dat_glad_edgi$dem.university_education_attend_school.txt)

```



#Save data
Vector for final variables to export
```{r variables to export}
export_variables <-
  c(
    "ID",
    "sample",
    "dem.university_education_attend_school.txt"
    )
```


Join datasets together
```{r GLAD columns export}
glad_dat.exp <- dat_glad_edgi %>%
  filter(sample == "GLAD") %>%
  select(all_of(export_variables))
glad_dat.exp
```

```{r EDGI columns export}
edgi_dat.exp <- dat_glad_edgi %>%
  filter(sample == "EDGI") %>%
  select(all_of(export_variables))
edgi_dat.exp
```



```{r GLAD EDGI NBR export}
glad_edgi_dat.exp <- dat_glad_edgi %>%
  filter(sample == "GLAD" | sample == "EDGI") %>%
  select(all_of(export_variables))
glad_edgi_dat.exp
```


Save data
```{r save GLAD, EDGI, GLAD&EDGI data}
saveRDS(object = 
  glad_edgi_dat.exp,
  file = paste0(ilovedata, "/data/2022-09-16/glad_edgi/demographics/", "years_of_education_GLAD_EDGI.rds"))
saveRDS(object = 
  glad_dat.exp,
  file = paste0(ilovedata, "/data/2022-09-16/glad/demographics/", "years_of_education_GLAD.rds"))
saveRDS(object = 
  edgi_dat.exp,
  file = paste0(ilovedata, "/EDGI_protocol/data/demographics/", "years_of_education_edgi_clean.rds"))

```
