---
title: 'EDGI protocol: Merging data'
author: "Helena Davies"
date: "24/08/2022"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in paths file}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovedata_scripts, "functions/add_numeric.R"))
source(file = paste0(ilovedata_scripts, "functions/remove_duplicates.R"))
source(file = paste0(ilovedata_scripts, "functions/sumscores.R"))
source(file = paste0(ilovedata_scripts, "functions/package_check.R"))
source(file = paste0(ilovedata_scripts, "functions/imp_check.R"))
source(file = paste0(ilovedata_scripts, "functions/recode_check.R"))
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in gender 
```{r read in gender sex and sexuality data}
sex_gender_sexuality <- readRDS(file = paste0(filepath_cleaned_data,
                                     "/demographics/sex_gender_sexuality_edgi_clean.rds"))
  
# Check
sex_gender_sexuality %>%
  colnames()

sex_gender_sexuality %>%
  dim()

# Select variables we need 
sex_gender_sexuality <- sex_gender_sexuality %>%
  select(ID,
         sample,
         dem.sex,
         demographics.what_gender_do_you_identify_with = dem.what_gender_do_you_identify_with,
         dem.what_is_your_sexual_orientation,
         dem.do_you_identify_as_transgender)
```

# Read in 'Ethnicity'
```{r read in ethnicity}
ethnicity <- readRDS(file = paste0(filepath_cleaned_data,
                                     "/demographics/ethnicity_edgi_clean.rds"))
  
# Check
ethnicity %>%
  colnames()

ethnicity %>%
  dim()

# Select variables we need 
ethnicity <- ethnicity %>%
  select(ID,
         dem.what_is_your_ethnic_origin)
```

# Education
```{r read in education}
education <- readRDS(file = paste0(filepath_cleaned_data,
                                     "/demographics/highest_education_edgi_clean.rds"))
  
# Check
education %>%
  colnames()

education %>%
  dim()

# Select variables we need 
education <- education %>%
  select(ID,
         dem.highest_education_finegrained)
```

```{r read in years of education}
years_of_education <- readRDS(file = paste0(filepath_cleaned_data,
                                     "/demographics/years_of_education_edgi_clean.rds"))
  
# Check
years_of_education %>%
  colnames()

years_of_education %>%
  dim()

# Select variables we need 
years_of_education <- years_of_education %>%
  select(ID,
         dem.university_education_attend_school.txt)
```

# Employment
```{r read in employment}
employment <- readRDS(file = paste0(filepath_cleaned_data,
                                     "/demographics/employment_edgi_clean.rds"))
  
# Check
employment %>%
  colnames()

employment %>%
  dim()

# Needs fixing
# Select variables we need 
employment <- employment %>%
  select(ID,
         dem.what_is_your_current_employment_status_numeric)

employment <- employment %>%
  mutate(dem.what_is_your_current_employment_status =
           case_when(dem.what_is_your_current_employment_status_numeric == 1 ~ "In paid employment or self-employed",
                     dem.what_is_your_current_employment_status_numeric == 2 ~ "Retired",
                     dem.what_is_your_current_employment_status_numeric == 3 ~ "Looking after home and/or family",
                     dem.what_is_your_current_employment_status_numeric == 4 ~ "Unable to work because of sickness or disability",
                     dem.what_is_your_current_employment_status_numeric == 5 ~ "Unemployed",
                     dem.what_is_your_current_employment_status_numeric == 6 ~ "Doing unpaid or voluntary work",
                     dem.what_is_your_current_employment_status_numeric == 7 ~ "Full-time or part-time student",
                     
                     dem.what_is_your_current_employment_status_numeric == 9 ~ "Other"
                     
                     ))

```

# Relationship status
```{r read in relationship status}
# Needs fixing
relationship_status <- readRDS(file = paste0(filepath_cleaned_data,
                                     "/demographics/marital_status_edgi_clean.rds"))
  
# Check
relationship_status %>%
  colnames()

relationship_status %>%
  dim()

# Select variables we need 
relationship_status <- relationship_status %>%
  select(ID,
         dem.what_is_your_current_maritalrelationship_status)
```

# Smoking status 
Note: This script needs further reviewing. HLD has done a quick review.
```{r read in smoking status}
smoking_status <- readRDS(file = paste0(filepath_cleaned_data,
                                     "/demographics/smoking_pack_year_edgi_clean.rds"))
  
# Check
smoking_status %>%
  colnames()

smoking_status %>%
  dim()

# Select variables we need 
smoking_status <- smoking_status %>%
  select(ID,
         dem.pack_year)
```

# Treatment
Note: For some reason, this is saved in the MHD even though it's part of the ED100K screening questionnaire.
```{r read in treatment data}
treatment <- readRDS(file = paste0(filepath_edgi_raw,
                                     "mhd_edgi.rds"))
  
# Check
treatment %>%
  colnames()

treatment %>%
  dim()

# Select variables we need 
treatment <- treatment %>%
  select(ID = externalDataReference,
         mhd.eating_disorder_received_treatment)
```

# Age
```{r read in age data}
age <- readRDS(file = paste0(filepath_cleaned_data,
                                     "/demographics/age_edgi_clean.rds"))
  
# Check
age %>%
  colnames()

age %>%
  dim()

# Select variables we need 
age <- age %>%
  select(ID,
         dem.how_old_are_you_now.txt,
         dem.dob_age,
         dem.age_category)

# Check
age %>%
  freq(dem.how_old_are_you_now.txt)

age %>%
  freq(dem.dob_age)

```

# Eating disorder diagnosis: algorithm-derived
```{r read in eating disorder algorithm data}
eating_disorder_algorithm <- readRDS(file = paste0(filepath_cleaned_data,
                                     "algorithms/ed_algorithms_diagnostics_edgi_clean.rds"))
  
# Check
eating_disorder_algorithm %>%
  colnames()

eating_disorder_algorithm %>%
  dim()

# Select variables we need 
eating_disorder_algorithm <- eating_disorder_algorithm %>%
  select(ID,
         ed.DSM5_AN_binary,
         ed.DSM5_AN_restricting_binary,
         ed.DSM5_AN_binge_purge_binary,
         ed.DSM5_BN_binary,
         ed.DSM5_BED_binary)
```

# Self-report (MHD)
```{r read in mhd data}
# Needs fixing
mhd1 <- readRDS(file = paste0(filepath_cleaned_data,
                                     "clinical/mhd_edgi_clean.rds"))
mhd1 <- mhd1 %>%
  select(-mhd.autism_spectrum_disorder)

mhd2 <- readRDS(file = paste0(filepath_edgi_raw,
                              "dem_edgi.rds"))

mhd2 <- mhd2 %>%
  select(ID = externalDataReference,
         mhd.autism_spectrum_disorder = dem.autism_spectrum_disorder_)

# Merge 
mhd <- dplyr::full_join(mhd1,
                        mhd2,
                        by = "ID")
              
# Check
mhd %>%
  colnames()

mhd %>%
  dim()

# Recode personality disorder - to fix
mhd <- mhd %>%
  mutate(mhd.personality_disorder_diagnosed =
           case_when(
           mhd.personality_disorder_numeric == 0 ~ "No personality disorder",
           mhd.personality_disorder_diagnosed_numeric == 1 ~ "Paranoid personality disorder",
          mhd.personality_disorder_diagnosed_numeric == 2 ~ "Schizoid personality disorder",
          mhd.personality_disorder_diagnosed_numeric == 3 ~ "Schizotypal personality disorder",
           mhd.personality_disorder_diagnosed_numeric == 4~ "Antisocial personality disorder",
            mhd.personality_disorder_diagnosed_numeric == 5~ "Borderline/Emotionally unstable, personality disorder",
             mhd.personality_disorder_diagnosed_numeric == 6~ "Histrionic personality disorder",
              mhd.personality_disorder_diagnosed_numeric == 7~ "Narcissistic personality disorder",
               mhd.personality_disorder_diagnosed_numeric == 8~ "Avoidant/anxious personality disorder",
                mhd.personality_disorder_diagnosed_numeric == 9~ "Dependent personality disorder",
                 mhd.personality_disorder_diagnosed_numeric == 10~ "Obsessive-compulsive personality disorder",
         mhd.personality_disorder_diagnosed_numeric == 11 ~ "Mixed personality disorder"
         
         )
  )

# Select columns
mhd <- mhd %>%
  select(#-endDate,
         #  -startDate,
           -sample)
```

# Somatic comorbidity
```{r read in somatic data}
somatic <- readRDS(file = paste0(filepath_cleaned_data,
                                     "/demographics/disability_illness_edgi_clean.rds"))
  
# Check
somatic %>%
  colnames()

somatic %>%
  dim()

# Select columns
somatic <- somatic %>%
  select(-endDate,
           -startDate,
           -sample)
```

# Age at diagnosis
```{r read in age at diagnosis data}
age_at_diagnosis <- readRDS(file = paste0(filepath_cleaned_data,
                                     "/demographics/age_at_diagnosis_edgi_clean.rds"))
  
# Check
age_at_diagnosis %>%
  colnames()

age_at_diagnosis %>%
  dim()
```

# OSFED / other diagnoses
```{r read in OSFED diagnoses}
OSFED_other_eating_disorders <- readRDS(file = paste0(filepath_cleaned_data,
                                     "/algorithms/osfed_dsm5_algorithms_edgi_clean.rds"))
  
# Check
OSFED_other_eating_disorders %>%
  colnames()

OSFED_other_eating_disorders %>%
  dim()
```

# Merge all data
```{r}
dat <- list(sex_gender_sexuality,
                ethnicity,
                education,
                years_of_education,
                employment,
                relationship_status,
                smoking_status,
                treatment,
                age,
                eating_disorder_algorithm,
                mhd,
                somatic,
                OSFED_other_eating_disorders,
                age_at_diagnosis
                ) %>%
  reduce(full_join,
         by = "ID")
```

# Look at the data
```{r view table}
skimr::skim(dat)

dat %>%
  colnames()

dat %>%
  dim()
```

# Save the data
```{r save the merged data}
dat %>% 
  saveRDS(
    file = paste0(filepath_cleaned_data, "merged_dat.rds")
    )

```

