---
title: "Demographics"
author: "Christopher Huebel, Helena Davies, Dina Monssen"
date: "2022-08-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear Global Environment
```{r clear global environment}
rm(list = ls(all.names = TRUE)) 
```

Read in file with path to data channel
```{r Read in file with path to data channel on teams}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovedata_scripts, "functions/add_numeric.R"))
source(file = paste0(ilovedata_scripts, "functions/remove_duplicates.R"))
source(file = paste0(ilovedata_scripts, "functions/sumscores.R"))
source(file = paste0(ilovedata_scripts, "functions/package_check.R"))
source(file = paste0(ilovedata_scripts, "functions/imp_check.R"))
source(file = paste0(ilovedata_scripts, "functions/recode_check.R"))
```

Load packages
```{r Load packages}
library(tidyverse)
library(flextable)
library(officer)
library(gtsummary)
```

Set current date
```{r current date}
date <- Sys.Date()
```

Load data
```{r Load data}
load(file = paste0(filepath_cleaned_data, "tables.Rdata"))
```

```{r}
names(dat_psych_dx)
```

```{r summary_table table}
dat_psych_dx$mhd.any_personality_disorder <- as.factor(dat_psych_dx$mhd.any_personality_disorder)

summary_table <-
  dat_psych_dx %>%
  gtsummary::tbl_summary(
        
        by =  mixed_eating_disorders_all,
        
        label = list(
        mhd.depression_and_anxiety ~
        "Depression and Anxiety",
        mhd.depressive_disorders ~
        "Depressive Disorders",
        mhd.anxiety_disorders ~
        "Anxiety Disorders",
        mhd.ptsd_numeric~
        "PTSD",
        mhd.obsessive_compulsive_disorders ~
        "Obessive Compulsive Disorders",
        mhd.any_personality_disorder ~
        "Personality Disorder",
        mhd.bipolar_and_schizophrenia ~
        "Bipolar Disorder and Schizophrenia", # why is Bipolar and SZ grouped here, but bipolar also appears below alone?
        mhd.psychotic_disorders ~
        "Psychotic Disorders",
        mhd.bipolar_disorder_numeric ~
        "Bipolar Disorder",
        mhd.autism_spectrum_disorder ~
        "ASD" # do we want consistency in whether we are spelling out in full or abbreviating?
         ),
                
          type = list(mhd.depression_and_anxiety ~
            "categorical",
          mhd.depressive_disorders ~
           "categorical",
          mhd.anxiety_disorders ~
            "categorical",
          mhd.ptsd_numeric~
            "categorical",
          mhd.obsessive_compulsive_disorders ~
            "categorical",
        mhd.any_personality_disorder ~
            "categorical",
        mhd.bipolar_and_schizophrenia ~
            "categorical",
        mhd.psychotic_disorders ~
            "categorical",
        mhd.bipolar_disorder_numeric ~
            "categorical",
        mhd.autism_spectrum_disorder ~
            "categorical" # do we want consistency in whether we are spelling out in full or abbreviating?
        ),
        missing = "ifany",
          digits = list(all_categorical() ~ c(0, 1)),
             statistic = list(
                             
            all_categorical() ~ "{n} ({p}%)"))

summary_table
```


```{r summary_table_long table}
dat_psych_dx_longer$mhd.any_personality_disorder <- as.factor(dat_psych_dx_longer$mhd.any_personality_disorder)

summary_table_long <-
  dat_psych_dx_longer %>%
  gtsummary::tbl_summary(
        
        by =  Disorder,
        
        label = list(
        mhd.depression_and_anxiety ~
        "Depression and anxiety",
        mhd.depressive_disorders ~
        "Depressive disorder/s",
        mhd.anxiety_disorders ~
        "Anxiety disorder/s",
        mhd.ptsd_numeric~
        "PTSD",
        mhd.obsessive_compulsive_disorders ~
        "Obessive compulsive disorder/s",
        mhd.any_personality_disorder ~
        "Personality disorder",
        mhd.bipolar_and_schizophrenia ~
        "Bipolar disorder and schizophrenia",
        mhd.psychotic_disorders ~
        "Psychotic disorders",
        mhd.bipolar_disorder_numeric ~
        "Bipolar disorder",
        mhd.autism_spectrum_disorder ~
        "ASD",
        mhd.addadhd_numeric ~
          "ADHD"
         ),
                
          type = list(mhd.depression_and_anxiety ~
            "categorical",
          mhd.depressive_disorders ~
           "categorical",
          mhd.anxiety_disorders ~
            "categorical",
          mhd.ptsd_numeric ~
            "categorical",
          mhd.obsessive_compulsive_disorders ~
            "categorical",
        mhd.any_personality_disorder ~
            "categorical",
        mhd.bipolar_and_schizophrenia ~
            "categorical",
        mhd.psychotic_disorders ~
            "categorical",
        mhd.bipolar_disorder_numeric ~
            "categorical",
        mhd.autism_spectrum_disorder ~
            "categorical",
        mhd.addadhd_numeric ~ 
          "categorical"
        ),
               missing = "ifany",
      #   value = list( mhd.depressive_disorders = "Depressive disorder",
      #             mhd.anxiety_disorders = "Anxiety disorder",
      #             mhd.ptsd_numeric = 1,
      #             mhd.obsessive_compulsive_disorders = "Obsessive compulsive disorder",
      #             mhd.any_personality_disorder = "Personality disorder",
      #             mhd.psychotic_disorders = "Psychotic disorder", 
      #             mhd.bipolar_disorder_numeric = 1,
      #             mhd.autism_spectrum_disorder = 1,
      #             mhd.addadhd_numeric = 1
      #             ),
          digits = list(all_categorical() ~ c(0, 1),
                          all_dichotomous() ~ c(0, 1)),
             statistic = list(
                             
            all_categorical() ~ "{n} ({p}%)"))


summary_table_long
```



Add bold labels to table
```{r summary_table with bold labels}
summary_table %>% 
  bold_labels() 
```

```{r summary_table_long with bold labels}
summary_table_long %>% 
  bold_labels() 
```

Save as a word document
```{r word properties}
sect_properties <- officer::prop_section(
  page_size = 
    page_size(
      orient = "landscape",
      width = 8.3,
      height = 11.7
      ),
  type = "continuous",
  page_margins = page_mar()
)
```

```{r summary_table as word document}
summary_table %>%
  as_flex_table() %>%
  flextable::save_as_docx(
    path = "../../results/supplement/EDGI_psychiatric_dx.docx",
    pr_section = sect_properties
  )
```

```{r summary_table_long as word document}
summary_table_long %>%
  as_flex_table() %>%
  flextable::save_as_docx(
    path = "../../results/main_manuscript/EDGI_psychiatric_dx_long_for_manuscript.docx",
    pr_section = sect_properties
  )
```

