---
title: "Demographics"
author: "Christopher Huebel, Helena Davies, Dina Monssen, Shannon Bristow"
date: "2022-09-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear Global Environment

```{r clear global environment}
rm(list = ls(all.names = TRUE)) 
```

Read in file with path to data channel
```{r Read in file with path to data channel on teams}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0("functions/add_numeric.R"))
source(file = paste0("functions/remove_duplicates.R"))
source(file = paste0("functions/package_check.R"))
```

Load packages

```{r Load packages}
library(tidyverse)
library(gtsummary)
```

Set current date

```{r current date}
date <- Sys.Date()
```

Load data

```{r Load data}
load(file = paste0(filepath_cleaned_data, "tables.Rdata"))
```


```{r}
names(dat_demographics)
```


```{r format table}
summary_table <-
  dat_demographics %>%
  gtsummary::tbl_summary(
        
        by =  mixed_eating_disorders,
        
        label = list(
       #dem sex is missing. is this a mistake?
          demographics.what_gender_do_you_identify_with ~
          "Gender",
        dem.what_is_your_sexual_orientation ~
          "Sexual Orientation",
        dem.do_you_identify_as_transgender ~
          "Transgender"
        dem.what_is_your_ethnic_origin, ~
          "Ethnic Origin"
        dem.highest_education_finegrained ~
          "Highest Education Level"
        #there was a gap between these in other script. do i need one here?
        dem.what_is_your_current_employment_status ~
          "Current Employment Status"
        dem.what_is_your_current_maritalrelationship_status ~
          "Current Marital/Relationship Status"
        dem.pack_year ~ # is this smoking?
          "Smoking status"
        mhd.eating_disorder_received_treatment ~
            "Received Treatment"
        ),
        
          type = list(demographics.what_gender_do_you_identify_with ~ 
            "categorical",
          dem.what_is_your_sexual_orientation ~
            "categorical",
          dem.do_you_identify_as_transgender ~
            "categorical"
          dem.what_is_your_ethnic_origin ~
            "categorical"
          dem.highest_education_finegrained ~
            "categorical"
          dem.what_is_your_current_employment_status ~
            "categorical"
          dem.what_is_your_current_maritalrelationship_status ~
            "categorical"          
          dem.pack_year ~ # is this smoking?
            "categorical"
          mhd.eating_disorder_received_treatment ~
            "categorical"
          ),

          statistic = list(
                             
            all_categorical() ~ "{n} ({p}%)",
            
            all_continuous2() ~ c("{mean} ({sd})",
                                  "{median} ({p25}, {p75})",
                                  "{min}, {max}"
                                  )
                ), 
              
              missing = "always")  %>% 
  add_n()
```


```{r format table}
summary_table <-
  dat_demographics_long %>%
  gtsummary::tbl_summary(
        
        by =  Disorder,
        
        label = list(
        demographics.what_gender_do_you_identify_with ~
          "Gender",
        dem.what_is_your_sexual_orientation ~
          "Sexual Orientation",
        dem.do_you_identify_as_transgender ~
          "Transgender"
      dem.what_is_your_ethnic_origin, ~
          "Ethnic Origin"
        dem.highest_education_finegrained ~
          "Highest Education Level"
        #there was a gap between these in other script. do i need one here?
        dem.what_is_your_current_employment_status ~
          "Current Employment Status"
        dem.what_is_your_current_maritalrelationship_status ~
          "Current Marital/Relationship Status"
        dem.pack_year ~ # is this smoking?
          "Smoking status"
        mhd.eating_disorder_received_treatment ~
            "Received Treatment"
          ),
                
          type = list(demographics.what_gender_do_you_identify_with ~ 
            "categorical",
          dem.what_is_your_sexual_orientation ~
            "categorical",
          dem.do_you_identify_as_transgender ~
            "categorical"
         dem.what_is_your_ethnic_origin ~
            "categorical"
          dem.highest_education_finegrained ~
            "categorical"
          dem.what_is_your_current_employment_status ~
            "categorical"
          dem.what_is_your_current_maritalrelationship_status ~
            "categorical"          
          dem.pack_year ~ # is this smoking?
            "categorical"
          mhd.eating_disorder_received_treatment ~
            "categorical"
           ),

          statistic = list(
                             
            all_categorical() ~ "{n} ({p}%)",
            
            all_continuous2() ~ c("{mean} ({sd})",
                                  "{median} ({p25}, {p75})",
                                  "{min}, {max}"
                                  )
                ), 
              
              missing = "always")  %>% 
  add_n()
```



Add bold labels to table

```{r table with bold labels}
summary_table %>% 
  bold_labels() 
```

Save as a word document

```{r table as word document}
summary_table %>%
  as_flex_table() %>%
  flextable::save_as_docx(
    path = "../results/EDGI_demographics.docx"
  )
```

