---
title: "Demographics"
author: "Christopher Huebel, Helena Davies, Shannon Bristow, Dina Monssen"
date: "2022-08-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear Global Environment

```{r clear global environment}
rm(list = ls(all.names = TRUE)) 
```

Read in file with path to data channel
```{r Read in file with path to data channel on teams}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0("functions/add_numeric.R"))
source(file = paste0("functions/remove_duplicates.R"))
source(file = paste0("functions/package_check.R"))
```

Load packages

```{r Load packages}
library(tidyverse)
library(gtsummary)
```

Set current date

```{r current date}
date <- Sys.Date()
```

Load data

```{r Load data}
load(file = paste0(filepath_cleaned_data, "tables.Rdata"))
```


```{r}
names(dat_psych_dx)
```


```{r format table}
summary_table <-
  dat_psych_dx %>%
  gtsummary::tbl_summary(
    
    by =  mixed_eating_disorders,
        
        label = list(
        mhd.depression_and_anxiety ~
        "Depression and Anxiety",
        mhd.depressive_disorders ~
        "Depressive Disorders",
        mhd.anxiety_disorders ~
        "Anxiety Disorders",
        mhd.ptsd_numeric~
        "PTSD",
        mhd.obsessive_compulsive_disorders ~
        "Obessive Compulsive Disorders",
        mhd.personality_disorder_diagnosed_numeric ~
        "Personality Disorder",
        mhd.bipolar_and_schizophrenia ~
        "Bipolar Disorder and Schizophrenia", # why is Bipolar and SZ grouped here, but bipolar also appears below alone?
        mhd.psychotic_disorders ~
        "Psychotic Disorders",
        mhd.bipolar_disorder_numeric ~
        "Bipolar Disorder",
        mhd.autism_spectrum_disorder ~
        "ASD" # do we want consistency in whether we are spelling out in full or abbreviating?
         ),
                
          type = list(
            mhd.depression_and_anxiety ~
            "categorical",
          mhd.depressive_disorders ~
           "categorical",
          mhd.anxiety_disorders ~
            "categorical",
          mhd.ptsd_numeric~
            "categorical",
          mhd.obsessive_compulsive_disorders ~
            "categorical",
        mhd.personality_disorder_diagnosed_numeric ~
            "categorical",
        mhd.bipolar_and_schizophrenia ~
            "categorical", # why is Bipolar and SZ grouped here, but bipolar also appears below alone?
        mhd.psychotic_disorders ~
            "categorical",
        mhd.bipolar_disorder_numeric ~
            "categorical",
        mhd.autism_spectrum_disorder ~
            "categorical" # do we want consistency in whether we are spelling out in full or abbreviating?
        ),

          statistic = list(
                             
            all_categorical() ~ "{n} ({p}%)",
            
            all_continuous2() ~ c("{mean} ({sd})",
                                  "{median} ({p25}, {p75})",
                                  "{min}, {max}"
                                  )
                ), 
              
              missing = "always")  %>% 
  add_n()
```

Add bold labels to table

```{r table with bold labels}
summary_table %>% 
  bold_labels() 
```

Save as a word document

```{r table as word document}
summary_table %>%
  as_flex_table() %>%
  flextable::save_as_docx(
    path = "../results/EDGI_psychiatric_dx.docx"
  )
```

