---
title: "Demographics"
author: "Christopher Huebel, Helena Davies, Shannon Bristow, Dina Monssen"
date: "2022-08-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear Global Environment

```{r clear global environment}
rm(list = ls(all.names = TRUE)) 
```

Read in file with path to data channel
```{r Read in file with path to data channel on teams}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0("functions/add_numeric.R"))
source(file = paste0("functions/remove_duplicates.R"))
source(file = paste0("functions/package_check.R"))
```

Load packages

```{r Load packages}
library(tidyverse)
library(gtsummary)
```

Set current date

```{r current date}
date <- Sys.Date()
```

Load data

```{r Load data}
load(file = paste0(filepath_cleaned_data, "tables.Rdata"))
```


```{r}
names(dat_somatic_dx)
```


```{r format table}
summary_table <-
  dat_somatic_dx %>%
  gtsummary::tbl_summary(
        
        by =  mixed_eating_disorders,
        
        label = list(
        dem.epilepsy_or_convulsions ~
          "Epilepsy or Convulsions",
        dem.migraines ~
          "Migraines",
        dem.multiple_sclerosis ~
          "Multiple Sclerosis",
        dem.parkinsons_disease ~
          "Parkinsons Disease",
        dem.severe_memory_loss ~
          "Severe Memory Loss",
        dem.neurological_none ~
          "No Neurological Condition", # is this naming ok?
        dem.neurological_dont_know ~
          "Neurological Condition Unknown", # is this naming ok?
        dem.neurological_prefer_not_to_answer ~ 
          "Neurological Prefer Not to answer",
        dem.hay_fever ~
          "Hay Fever",
        dem.drug_allergy ~                                                 
          "Drug Allergy",                                               
        dem.food_allergy ~
          "Food Allergy",
        dem.food_allergy_txt ~ # do we want to keep the free text responses?
          "Other Food Allergy", #not sure if this is the right wording?
        dem.other_allergy ~
          "Other Allergies",
#        dem.other_allergy_txt # do we want to keep the free text responses?                                          
        dem.osteoporosis ~
          "Osteoporosis",
        dem.osteoarthritis ~
          "Osteoarthriris",
        dem.rheumatoid_arthritis ~
          "Rheumatoid Arthritis",
        dem.other_arthritis ~
          "Any Other Arthritis",
        dem.other_arthritis_txt ~ # do we want the free text response?
          "Any Other Arthritis Free Text",
        dem.allergy_none ~
          "No Allergies",
        dem.allergy_prefer_not_to_answer ~
          "Allergy Prefer Not to Answer",
        dem.allergy_dont_know ~    
          "Allergies Unknown",
        dem.asthma ~
          "Asthma",
        dem.emphysema_or_chronic_bronchitis ~
          "Emphysema or Chronic Bronchitis",
        dem.heart_attack_or_angina ~
          "Heart Attack or Angina",
        dem.high_blood_cholesterol ~
          "High Cholesterol",
        dem.high_blood_pressure ~   
          "High Blood Pressure",
        dem.atrial_fibrillation ~
          "Atrial Fibrillation",
        dem.stroke ~
          "Stroke",
        dem.respiratory_none ~
          "No Respiratory Condition",
        dem.respiratory_prefer_not_to_answer ~    
          "Respiratory Prefer Not to Answer",
        dem.respiratory_dont_know ~
          "Respiratory Condition Unknown",
        dem.crohns_disease ~
          "Chron's Disease",
        dem.ulcerative_colitis ~
          "Ulcerative Colitis",
        dem.coeliac_disease ~
          "Coeliac disease",
        dem.diabetes_type_1 ~
          "Diabetes Type 1",
        dem.diabetes_type_2 ~   
          "Diabetes Type 2",
        dem.pain_due_to_diabetes ~
          "Diabetic-related Pain",
        dem.pain_due_to_virus ~
            "Viral-related pain",
        dem.digestive_none ~
          "No Digestive Conditions",
        dem.digestive_dont_know ~
          "Digestive Condition Unknown",
        dem.digestive_prefer_not_to_answer ~
          "Digestive prefer not to answer",
        dem.breast_cancer ~
          "Breast Cancer",
        dem.lung_cancer ~
          "Lung Cancer",
        dem.stomach_cancer ~
          "Stomach Cancer",
        dem.colon_cancer ~
          "Colon Cancer",
        dem.uterus_cancer ~
          "Uterus Cancer",
        dem.prostate_cancer ~
          "Prostate Cancer",
        dem.cancer_none ~
          "No Cancer",
        dem.cancer_dont_know ~
          "Cancer Unknown",
        dem.cancer_prefer_not_to_answer ~
          "Cancer Prefer Not to Answer",
        dem.psoriasis ~
          "Psoriasis",
        dem.vitiligo ~
          "Vitiligo",
        dem.eczema ~
          "Eczema",
        dem.thyroid_disease ~
          "Thyroid Disease",
        dem.thyroid_disease_txt ~
          "Thyroid Disease Free Text Responses",
        dem.skin_none ~
          "No Dermatological Conditions",
        dem.skin_dont_know ~
          "Dermatological Conditions Unknown",
        dem.skin_prefer_not_to_answer ~
          "Dermatological Prefer Not to Answer"
        ),
                
          type = list(
            dem.epilepsy_or_convulsions ~
          "categorical",
        dem.migraines ~
          "categorical",
        dem.multiple_sclerosis ~
          "categorical",
        dem.parkinsons_disease ~
          "categorical",
        dem.severe_memory_loss ~
          "categorical",
        dem.neurological_none ~
          "categorical", # is this naming ok?
        dem.neurological_dont_know ~
          "categorical", # is this naming ok?
        dem.neurological_prefer_not_to_answer ~ 
          "categorical",
        dem.hay_fever ~
          "categorical",
        dem.drug_allergy ~                                                 
          "categorical",                                               
        dem.food_allergy ~
          "categorical",
        dem.food_allergy_txt ~ # do we want to keep the free text responses?
          "categorical", #not sure if this is the right wording?
        dem.other_allergy ~
          "categorical",
#        dem.other_allergy_txt # do we want to keep the free text responses?                                          
        dem.osteoporosis ~
          "categorical",
        dem.osteoarthritis ~
          "categorical",
        dem.rheumatoid_arthritis ~
          "categorical",
        dem.other_arthritis ~
          "categorical",
        dem.other_arthritis_txt ~ # do we want the free text response?
          "categorical",
        dem.allergy_none ~
          "categorical",
        dem.allergy_prefer_not_to_answer ~
          "categorical",
        dem.allergy_dont_know ~    
          "categorical",
        dem.asthma ~
          "categorical",
        dem.emphysema_or_chronic_bronchitis ~
          "categorical",
        dem.heart_attack_or_angina ~
          "categorical",
        dem.high_blood_cholesterol ~
          "categorical",
        dem.high_blood_pressure ~   
          "categorical",
        dem.atrial_fibrillation ~
          "categorical",
        dem.stroke ~
          "categorical",
        dem.respiratory_none ~
          "categorical",
        dem.respiratory_prefer_not_to_answer ~    
          "categorical",
        dem.respiratory_dont_know ~
          "categorical",
        dem.crohns_disease ~
          "categorical",
        dem.ulcerative_colitis ~
          "categorical",
        dem.coeliac_disease ~
          "categorical",
        dem.diabetes_type_1 ~
          "categorical",
        dem.diabetes_type_2 ~   
          "categorical",
        dem.pain_due_to_diabetes ~
          "categorical",
        dem.pain_due_to_virus ~
            "categorical",
        dem.digestive_none ~
          "categorical",
        dem.digestive_dont_know ~
          "categorical",
        dem.digestive_prefer_not_to_answer ~
          "categorical",
        dem.breast_cancer ~
          "categorical",
        dem.lung_cancer ~
          "categorical",
        dem.stomach_cancer ~
          "categorical",
        dem.colon_cancer ~
          "categorical",
        dem.uterus_cancer ~
          "categorical",
        dem.prostate_cancer ~
          "categorical",
        dem.cancer_none ~
          "categorical",
        dem.cancer_dont_know ~
          "categorical",
        dem.cancer_prefer_not_to_answer ~
          "categorical",
        dem.psoriasis ~
          "categorical",
        dem.vitiligo ~
          "categorical",
        dem.eczema ~
          "categorical",
        dem.thyroid_disease ~
          "categorical",
        dem.thyroid_disease_txt ~
          "categorical",
        dem.skin_none ~
          "categorical",
        dem.skin_dont_know ~
          "categorical",
        dem.skin_prefer_not_to_answer ~
          "categorical"
        ),

          statistic = list(
                             
            all_categorical() ~ "{n} ({p}%)",
            
            all_continuous2() ~ c("{mean} ({sd})",
                                  "{median} ({p25}, {p75})",
                                  "{min}, {max}"
                                  )
                ), 
              
              missing = "always")  %>% 
  add_n()
```

Add bold labels to table

```{r table with bold labels}
summary_table %>% 
  bold_labels() 
```

Save as a word document

```{r table as word document}
sect_properties <- officer::prop_section(
  page_size = officer::page_size(
    orient = "landscape",
    width = 8.3,
    height = 11.7
    ),
  type = "continuous",
  page_margins = officer::page_mar()
)

summary_table %>%
  as_flex_table() %>%
  flextable::save_as_docx(
    path = "../results/EDGI_somatic_dx.docx", 
    pr_section = sect_properties
  )
```



