---
title: "Demographics"
author: "Shannon Bristow, Christopher Huebel, Helena Davies, Dina Monssen"
date: '2022-09-07'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear Global Environment

```{r clear global environment}
rm(list = ls(all.names = TRUE)) 
```

Read in file with path to data channel
```{r Read in file with path to data channel on teams}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0("functions/add_numeric.R"))
source(file = paste0("functions/remove_duplicates.R"))
source(file = paste0("functions/package_check.R"))
```

Load packages

```{r Load packages}
library(tidyverse)
library(gtsummary)
library(sm)
```

Set current date

```{r current date}
date <- Sys.Date()
```

Load data

```{r Load data}
load(file = paste0(filepath_cleaned_data, "tables.Rdata"))
```


```{r}
names(dat_demographics)
```

# Figures:  Age distribution of EDGI UK sample by age range and sex
```{r select age distribution data}
age_sex_distribution <- dat %>%
  select(
    mixed_eating_disorders,
         dem.dob_age, 
         dem.sex)

age_sex_distribution %>%
  names()
```

There is a problem in the age cleaning script. It creates lots of IDs that do not have matching IDs

```{r}
dat %>%
  filter(
    is.na(dem.sex)
  )
```




```{r}
dat %>%
  summarytools::freq(dem.sex)
```


```{r}
dat %>%
  filter(
    !is.na(dem.sex)
  ) %>%
  ggplot(aes (x = dem.dob_age, fill = dem.sex)) + 
  geom_density()
```



```{r}
dat %>%
  sm.density.compare(
    x = dem.dob_age,
    group = dem.sex
    )
```


```{r}
# Long format
exclude_columns_from_pivoting <-
  c(
    "dem.dob_age",
    "dem.sex"
    )

age_sex_distribution_long <- dat %>%
  select(
    all_of(exclude_columns_from_pivoting),
         
        # Disorder
        anorexia_nervosa,
        bulimia_nervosa,
        binge_eating_disorder
        ) %>%
  pivot_longer(
    -exclude_columns_from_pivoting,
#    names_to = "Old_variable",
    values_to = "Disorder"
    ) %>%
  select(
    -name
  )

age_sex_distribution_long
```



Add bold labels to table

```{r table with bold labels}
summary_table %>% 
  bold_labels() 
```

Save as a word document

```{r table as word document}
summary_table %>%
  as_flex_table() %>%
  flextable::save_as_docx(
    path = "../results/EDGI_demographics.docx"
  )
```

